### 2017-07-10 paper.tex
initial commit

\def\year{2017}\relax
%File: formatting-instruction.tex
\documentclass[letterpaper]{article} %DO NOT CHANGE THIS
\usepackage{aaai17}  %Required
\usepackage{times}  %Required
\usepackage{helvet}  %Required
\usepackage{courier}  %Required
\usepackage{url}  %Required
\usepackage{graphicx}  %Required
\frenchspacing  %Required
\setlength{\pdfpagewidth}{8.5in}  %Required
\setlength{\pdfpageheight}{11in}  %Required
%PDF Info Is Required:
  \pdfinfo{
/Title (Supervised Reinforcement Learning with Partial States: a Teaching Method for Action Selection for HRI)
/Author (Emmanuel Senft)}
\setcounter{secnumdepth}{0}  
 \begin{document}
% The file aaai.sty is the style file for AAAI Press 
% proceedings, working notes, and technical reports.
%
\title{Supervised Reinforcement Learning with Partial States: \\
 a Teaching Method for Action Selection for HRI}

\author{Emmanuel Senft \and S\'{e}verin Lemaignan\\
Centre for Robotics and Neural Systems \\
Plymouth University \\
United Kingdom\\
\And Paul Baxter\\
L-CAS\\
University of Lincoln\\
United Kingdom\\
 \And Tony Belpaeme\\
 CNRS\\ Plymouth University (UK) \\ iMinds \\ Ghent University (Be)}

\maketitle
\begin{abstract}
Robots are expected to be pervasive in human society in the future

not possible to hardcode everything by hand

requirement for learning

hard to learn for HRI
\begin{itemize}
	\item real time
	\item cost of exploration (real humans)
	\item no clear reward policy and cannot request a human to reward everything
	\item need to make the most out of each sample
\end{itemize}

Partial state RL

\end{abstract}
%===============================================================================

\section{Introduction}

Robot interacting with humans, bla bla bla

State used for action selection can be from different sensors, continuous, discrete, representing a value or a state

\cite{kober2013reinforcement}
%===============================================================================

\section{Background}
\subsection{Reinforcement Learning}
\subsection{Human enhanced Reinforcement Learning}
One of the main challenge when applying RL to robotics is poor perfermance in
 the early stages of the learning as the agent has to explore the environment to
 gather initial knowledge. This challenge is especially
important for robotics as trials often have to happen in the real world (as
simulator close enough to the real world as not available) and as such can
present risks for the robot or for the persons interacting with it.

%===============================================================================

\section{Proposition}
\subsection{Supervised Progressively Automous Robot Competencies}

\subsection{Partial-State Supervised Reinforcement Learning}

%===============================================================================
\section{Methodology}

A human supervisor can .
%===============================================================================
\section{Results}
%===============================================================================
\section{Conclusion}
\label{sec:conclusion}
%==============================================================================
\section{Acknowledgments}
This work was supported by the EU FP7 DREAM project (grant no.  611391) and EU
H2020 Marie Sklodowska-Curie Actions project DoRoThy (grant 657227).

\bibliographystyle{aaai} \bibliography{biblio}
\end{document}

### 2017-07-10 paper.tex
update with part of method

@@
 \usepackage{graphicx}  %Required
+\usepackage[ruled,vlined]{algorithm2e}
 \frenchspacing  %Required
@@
 
-Partial state RL
+Partial state RL - accelerate learning
 
@@
 \section{Proposition}
-\subsection{Supervised Progressively Automous Robot Competencies}
+\subsection{Supervised Progressively Autonomous Robot Competencies}
+
+As a way to enable a human supervisor to teach a robot an action policy while
+interacting with its environment, we proposed the Supervised Progressively
+Autonomous Robot Competencies (SPARC) in \cite{senft2015sparc}. SPARC is independent
+of the learning algorithm used, but define an interaction dynamic between an
+agent learning an action policy while interacting in an environment and a
+supervisor teaching this agent an action policy. The main goal of SPARC is
+enabling a robot to learn from a supervisor while ensuring that every action
+executed by the robot has approval of the supervisor but without requiring this
+supervisor to manually enforce every single action.
+
+The main concept in SPARC is giving the supervisor the control over the agent
+action and combine this with online learning on the agent side. This control is
+achieved using a suggestion/correction mechanism whereas the agent is presenting
+to the supervisor the action about to be executed and the supervisor can cancel
+this action before its execution or not doing anything, letting the action being
+executed after a delay. Additionally, the supervisor can select actions to be
+executed by the agent. The actions selected or canceled by the supervisor can be
+used as input with the current state by a learning algorithm to progressively
+improve the future suggestions.
+
+Giving power to an expert to correct the actions of the agent before the
+execution can ensure that even in the early phases of the learning the agent can
+have an appropriate action policy for the current environment as shown in Figure~\ref{fig:comparison}.
+
+\begin{figure}
+    \centering
+    \includegraphics[width=0.9\linewidth]{./fig/motivation.pdf}
+    \caption{Idealised expectation for performance, autonomy and workload for a
+    Wizard of Oz, a autonomous learner and SPARC.}
+    \label{fig:comparison}
+\end{figure}
+
+SPARC has been design with the idea of teaching a robot to interact with humans,
+it is specially usefull when the pace of action selection is low (less than
+1Hz), when the agent has to learn with a limited number of datapoints and when
+undesired actions executed by an agent can have a high cost.
+
+In \cite{senft2017supervised}, we presented a way to combine SPARC and RL, by
+assigning a positive reward to every action executed by the robot as it would
+have been passively or actvely validated by the supervisor. However this method
+was not making use of any type of generalisation, it was directly mapping a
+single state action pair to a reward.
 
 \subsection{Partial-State Supervised Reinforcement Learning}
+
+REFORMULATE: start with size of the world
+To be usable in complex environments, a
+learning algorithm requires generalisation as exactly identical spaces might
+never been observed twice.
+
+A classical approach to generalise in RL is to use a first layer of neural
+network or to use deep reinforcement learning which relies on deep neural
+networks to learn a mapping state-action-Qvalue for example. (ADDREF)
+These approaches, neural network based, relies on having a large number of
+datapoints to converge toward a good function approximator. However, as
+discussed previously, in many application, these amounts of data are not
+possible to be obtained and a robot might need to adapt to different persons and
+be retrained quickly.
+
+With that idea in mind, we propose to make a better use of human inputs, and ask
+ the supervisor to identify which features of the environment are linked to the
+ current selected action. That was, instead of having an state-action pair, we
+ can have a partial-state action pair, with this partial-state being a subset of
+ the state domain.
 
@@
 
-A human supervisor can .
+\subsection{Supervisation}
+Similarly to a SPARC setup, the supervisor is presented with action about to be
+executed by the robot and can either cancel it or let it be executed and the 
+supervisor has the possibility to select actions for the robot to execute.
+
+In addition to these actions, the supervisor can use the GUI to select features
+of the environment that can send to the algorithm to reduce the state associated
+to this action to a partial-state. Similarly, the algorithm can indicate which
+parts of the states have been used for the selection to the supervisor who can
+correct them while the action is being executed.
+
+Example?
+
+\subsection{Learning algorithm}
+
+In a first approach, the presence of an expert supervisor who can evaluate the
+expected future impacts of an action removes the problem of credit assignment
+for delayed rewards and allows us to consider only a myopic approach. (can cite
+kobers I think.)
+
+For this paper, we will reuse the formalism of rewardless Markov Decision 
+Process to identify the different elements of our system. The agent has action
+to a set of actions A, a state S (represented as a vector of n dimensions of
+values $\in [0;1]$). With each dimension of S representing features in the
+environment.
+
+At the state $s_{t}$ the agent receives the action $a_{i}$ with the partial
+state $s'$ defined in a subspace $S' \subseteq S$ (defined by selecting only a
+number $n' \leq n$ of the dimensions of S). For example, a state s could be
+defined in 4 dimensions such as $s=[1,0.2,0,0.5]$, and s' in two dimensions with
+$s'=[-,0.2,0,-]$ with symbol '-' reprensenting the dimensions removed.
+
+We store in memory the partial-state action pair $s'-a_{i}$, with the reward 1
+as the action has been selected by the supervisor. Similarly, if an action has
+been canceled by the supervisor, the partial-state action will be assigned to a
+reward $-1$.
+
+After interacting with the system under the supervisors control, the actions
+will have associated to each action $a \in A$, a collection $C_{a}$ of pairs
+partial-state-reward. When facing a new state $s$ where an action has to be
+selected, the agent can select an action following Algorithm \ref{algo}.
+
+\begin{algorithm}
+    \DontPrintSemicolon
+    \SetKwInOut{Input}{inputs}\SetKwInOut{Output}{output}
+    \Input{Current state s, action-partial state rewards tuples}
+    \Output{selected action $\pi(s)$}
+    \ForEach{a $\in $ A}{
+        \ForEach{ s'-r $\in C_{a}$}{
+            compute similarity
+            $\Delta(s',s)=1-\frac{\sum_{j}^{n'}(s'(j)-s(j))^{2}}{n'}$
+        }
+        $\Delta(a)=max(\Delta)$
+
+        $r(a)=R(argmax_{s'} \Delta(s'))$
+    }
+    $\pi(s) = argmax_{a}\Delta(a) \cdot r(a)$
+
+    \caption{Algorithm for selecting an action based on previous
+    partial-state action rewards tuples and current state}
+    \label{algo}
+\end{algorithm}
+
+When proposing an action following Algorithm~\ref{algo}, the agent can also use
+the dimensions of the similar state s' to indicate the supervisor which parts of
+the states have been used for the action selection.
+
 %===============================================================================
 \section{Results}
+
+\section{Future work}
+
+This method still has to be tested in a real Human-Robot Interaction, and this
+evaluation is currently being implemented and will be tested in a near future.
+
+Other way of extending the current work would be to combine it with the
+possibility of letting the agent continue to explore in the absence of a
+supervisor around a learnt action policy to keep improving its behaviour. This
+could be done by allowing the supervisor to provide rewards during the learning
+phase, rewards which could also be assigned to partial states. The system could
+also learn to predict these rewards in an approach similar to TAMER 
+\cite{knox2009interactively}. But in the case of an absence of supervisor, the assumption that only a
+myopic action selection is sufficient would not hold anymore and the problem of
+delayed rewards would have to be tackled. It could be for example possible to
+adapt well known algorithms such as QLearning to handle partial states rather
+the full states.
+
 %===============================================================================

### 2017-07-11 paper.tex
update background

@@
 
-Robot interacting with humans, bla bla bla
+Human-Robot Interaction (HRI) aims at having humans and robot living together
+in the society, interacting socially in many different environments and
+contexts. Robot are expected to behave appropriately regardless of the domain
+of interaction. However, not all behaviours are known in advance and can be
+implemented in the robot before its deployment in the real world. Robots need
+to be able to learn new tasks, new actions policies, new social norms and how
+to make sense of the world surrounding them.
+
+When interacting in the real world, humans face huge spaces of almost unlimited
+dimensions, and despite this complexity, adults and even more children are able
+to learn quickly, often from only a few demonstrations or examples. Humans are
+able to take the most out of every datapoint availble to them. On the other
+hand, recent advances in Machine Learning such as Deep Learning \cite{lecun2015deep}
+have been made possible by the availability of huge dataset covering millions
+of labeled examples or dozens of hours recording. These progress have
+targetting either perception, where labeled datapoints can be available or
+action selection in virtual environments where the impact of actions is
+limited.
+
+Similarly to humans, robots interacting in the real world will have to be able
+to learn quickly, from different types of inputs: demonstrations, commands,
+rewards and also autonomously.
 
@@
 \subsection{Reinforcement Learning}
+
+The main framework to provide a robot with autonomous learning is Reinforcement
+Learning (RL)(\cite{kober2013reinforcement,sutton1998reinforcement}. The main idea
+behind reinforcement learning is that a agent is interacting in an environment
+providing positive or numerical reward in reaction to the agent's actions and
+the agent selects actions to maximise the expected cummulative discounted
+reward.
+
+Classic approaches RL relies on exploring virtual environments where the agent
+tries to maximise the reward, but where in the end exploration often do not
+have a real impact and where the agent can interact as long as needed to gather
+enough information on the environment to find a correct action policy.
+
+But in many real worl problem, relying only on random exploration to obtain
+knowledge on the environment is not enough, the agent needs to have some initial
+knowledge or additional knowledge provided often by humans to  work more
+efficiently and achieve more complex results.
+
 \subsection{Human enhanced Reinforcement Learning}
+\subsubsection{Initial knowledge}
+One way to use human knowledge to help an agent to learn is through providing
+initial knowledge. 
+alphago
+
+IRL
+
+OpenAI deep RL
+
 One of the main challenge when applying RL to robotics is poor perfermance in
@@
 present risks for the robot or for the persons interacting with it.
+
+\subsubsection{Guiding the learning}
+scafolding 
+shaping
+guidance
 
@@
     \Output{selected action $\pi(s)$}
-    \ForEach{a $\in $ A}{
-        \ForEach{ s'-r $\in C_{a}$}{
+    \ForEach{a $\in$ A}{
+        \ForEach{s'-r $\in C_{a}$}{
             compute similarity
@@
 %===============================================================================
-\section{Results}
+\section{Challenges}
+
+The main challenge for using Interactive Machine Learning is to translate the
+state-action space between the human view and the algorithm view. This is one
+important reason why many researchers in IML focuse on limiting the human impact
+to providing reward~\cite{knox2009interactively} or kinesthetic demonstrations
+in the robot space~\cite{billard2008robot}. However as shown by Thomaz and Breazeal~\cite{thomaz2008teachable}, using more complex inputs from the supervisor, such
+as guidance biasing the action selection can lead to a better performance in the
+learning. But to able to use these higher level and more complex inputs from
+humans, these actions have to be translated in inputs usable for the learning
+algorithm and/or the action selection mechanism.
+
+The more complex the inputs from the humans are the more additional information
+can be transmitted to the learning, allowing the agent to learn more complex
+behaviours faster.
+
+Similarly, as shown by Senft and al. in \cite{senft2017supervised}, providing
+more control to the supervisor about the robot actions can lead to keep the
+agent in relevant states of the environment and as such speeding the learning
+and making it safer for the robot and people interacting with it. However this
+method is dependent of letting the human know what action the robot is about to
+execute, which relies on the robot to express its intention in a human
+understandable way. (ADDREF - see Serge?)
+
+Another challenge is state representation, the state accessed by the learning
+algorithm and the one accessed by the supervisor can be represented is highly
+different space, covering different features, and if the robot aims to profit
+from the human initial knowledge, it needs to have access to similar features in
+the environment to the ones the human is using, and the human needs to be able
+to transmit these features to the learning algorithm.
+(the representation of the state is often engineered by the programmers of the
+algorithm, and space features not considered in the initial design could
+actually be important in the final one. Idea of Deep Learning, but not enough
+datapoints.)
+
+Needs a parallel to human learning from humans
 

### 2017-07-13 paper.tex
Update

@@
 
-\author{Emmanuel Senft \and S\'{e}verin Lemaignan\\
-Centre for Robotics and Neural Systems \\
+\author{Emmanuel Senft \\
+CNRS \\
+Plymouth University \\
+United Kingdom\\
+\And S\'{e}verin Lemaignan\\
+CNRS \\
 Plymouth University \\
@@
 contexts. Robot are expected to behave appropriately regardless of the domain
-of interaction. However, not all behaviours are known in advance and can be
-implemented in the robot before its deployment in the real world. Robots need
+of interaction. However, not all behaviours can be known in advance and can be
+implemented in the robot before its deployment in the real world. Similarly to
+ humans, robots need
 to be able to learn new tasks, new actions policies, new social norms and how
@@
 to learn quickly, often from only a few demonstrations or examples. Humans are
-able to take the most out of every datapoint availble to them. On the other
-hand, recent advances in Machine Learning such as Deep Learning \cite{lecun2015deep}
+able to take the most out of every datapoint available to them. On the other
+hand, recent impressive advances in Machine Learning such as Deep Learning~\cite{lecun2015deep}
 have been made possible by the availability of huge dataset covering millions
-of labeled examples or dozens of hours recording. These progress have
+of labeled examples or dozens of hours of recording. These progress have
 targetting either perception, where labeled datapoints can be available or
@@
 Similarly to humans, robots interacting in the real world will have to be able
-to learn quickly, from different types of inputs: demonstrations, commands,
-rewards and also autonomously.
+to learn quickly. One way of achieving this fast learning is to learn from
+humans, i.e using human inputs to boostrap the learning. We argue that to be
+capable to interact in the real world with humans, robots have to be able to
+learn from different types of inputs: demonstrations, commands, rewards and 
+also autonomously.
 
-State used for action selection can be from different sensors, continuous, discrete, representing a value or a state
-
-\cite{kober2013reinforcement}
 %===============================================================================
@@
 The main framework to provide a robot with autonomous learning is Reinforcement
-Learning (RL)(\cite{kober2013reinforcement,sutton1998reinforcement}. The main idea
-behind reinforcement learning is that a agent is interacting in an environment
+Learning (RL)~\cite{kober2013reinforcement,sutton1998reinforcement}. In RL, an
+agent is interacting in an environment
 providing positive or numerical reward in reaction to the agent's actions and
-the agent selects actions to maximise the expected cummulative discounted
-reward.
+the agent learns an action policy to maximise the expected cummulative discounted
+reward obtained by the agent.
 
 Classic approaches RL relies on exploring virtual environments where the agent
-tries to maximise the reward, but where in the end exploration often do not
-have a real impact and where the agent can interact as long as needed to gather
-enough information on the environment to find a correct action policy.
-
-But in many real worl problem, relying only on random exploration to obtain
-knowledge on the environment is not enough, the agent needs to have some initial
-knowledge or additional knowledge provided often by humans to  work more
-efficiently and achieve more complex results.
+tries to maximise the reward. In most of the cases where RL achieves success, it
+had access to a virtual environment where the only real cost of exploring was
+time and energy, and the agent can interact as long as needed to gather
+enough information on the environment to find a correct action policy. When
+these conditions are reunited, RL can achieve impressive results, as shown by
+the victory of a computer in Backgammon back in the 90s~\cite{tesauro1995temporal} or more recently the success achieved in playing
+Atari games based only on the image and the game rewards~\cite{mnih2015human}.
 
 \subsection{Human enhanced Reinforcement Learning}
+
+No simulator of world, and especially of social interactions allows robots to 
+learn in a virtual environment, so robots, especially if the have to interact
+with humans have to be able to learn in the real world.
+However, in the real physical world, every actions have an impact on the
+environment, especially in HRI when actions can upset and negatively impact
+humans interacting with the robot. Additionally acquiring datapoints in can be
+expensive in term of time and other ressources. As such many approaches aiming
+at providing robot with learn to interact in the real world have relied on
+knowledge provided by a human in different way to avoid this random exploration
+presenting risk to the robot and persons interacting with it.
+
 \subsubsection{Initial knowledge}
 One way to use human knowledge to help an agent to learn is through providing
-initial knowledge. 
-alphago
+initial knowledge. By providing demonstrations of an expected actions policy,
+humans can boostrap the learning and provide the agent with a more appropriate
+action policy that it can improve over time.
 
-IRL
+These demonstrations can be used to create an initial action policy which could
+have been discovered autonomously, but without requiring an initial discovery
+phase where the performance has to be low when the agent is learning from its
+environment. Recent work~\cite{hester2017learning} have shown that using initial
+human demonstrations can allow the initial performance to be much better than
+starting from scratch in playing Atari games, and even sometimes this allow to
+achieve higher performance than only relying on exploration to learn an action
+policy.
 
-OpenAI deep RL
+In some cases, the state space is too big to rely only on random exploration to
+reach a successful action policy. For example the game of Go in its larger board
+size contains more than $10^{210}$ states, so exhaustive search is not possible
+with today's ressources. Authors of \cite{silver2016mastering} started with
+supervised learning from go master's games to learn a decent policy and then
+used convolutional networks, self play and tree search to achieve super-human
+capabilities and beatting humans best players.
 
-One of the main challenge when applying RL to robotics is poor perfermance in
-the early stages of the learning as the agent has to explore the environment to
-gather initial knowledge. This challenge is especially
-important for robotics as trials often have to happen in the real world (as
-simulator close enough to the real world as not available) and as such can
-present risks for the robot or for the persons interacting with it.
+Another way to use these demonstrations is Inverse
+Reinforcement Learning, the agent derives from demonstrations of an expert an
+expected reward function that it can use to improve a policy based on the
+demonstrations and so achieving higher performance than the demonstrations
+themselves. By using this technic, Abbeel managed to teach an autonomous
+helicopter to do high level acrobatics often only executable by high level
+expert~\cite{abbeel2004apprenticeship}.
+
+%One of the main challenge when applying RL to robotics is poor perfermance in
+%the early stages of the learning as the agent has to explore the environment to
+%gather initial knowledge. This challenge is especially
+%important for robotics as trials often have to happen in the real world (as
+%simulator close enough to the real world as not available) and as such can
+%present risks for the robot or for the persons interacting with it.
 
 \subsubsection{Guiding the learning}
-scafolding 
+Rather than providing initial knowledge to the agents, humans can also guide the
+agent throughout the learning by organising the tasks the robot will face, this
+approach is known as scaffolding \cite{saunders2006teaching}. This allows to
+teach the robot successive more complex policies by increasing the complexity of
+the task presented and reusing previously learnt behaviours.
+
 shaping
@@
 was not making use of any type of generalisation, it was directly mapping a
-single state action pair to a reward.
+single state action pair to a reward, and as such has limited efficiency in
+environments with a continuous space or a high dimensional and undeterministic
+one.
 
@@
 
-REFORMULATE: start with size of the world
+REFORMULATE: start with size of the world and oragnisation by sensory inputs
 To be usable in complex environments, a
 learning algorithm requires generalisation as exactly identical spaces might
-never been observed twice.
+never been observed twice in the life time of the agent.
 
@@
 network or to use deep reinforcement learning which relies on deep neural
-networks to learn a mapping state-action-Qvalue for example. (ADDREF)
+networks to learn a mapping state action Qvalue for example. (ADDREF)
 These approaches, neural network based, relies on having a large number of
@@
 the supervisor to identify which features of the environment are linked to the
- current selected action. That was, instead of having an state-action pair, we
+current selected action. Instead of having an state-action pair, we
 can have a partial-state action pair, with this partial-state being a subset of

### 2017-07-14 paper.tex
abstract

@@
 \begin{abstract}
-Robots are expected to be pervasive in human society in the future
-
-not possible to hardcode everything by hand
-
-requirement for learning
-
-hard to learn for HRI
-\begin{itemize}
-	\item real time
-	\item cost of exploration (real humans)
-	\item no clear reward policy and cannot request a human to reward everything
-	\item need to make the most out of each sample
-\end{itemize}
-
-Partial state RL - accelerate learning
-
+As robots will integrate human society, they will be expected to interact
+appropriately with surrounding humans. However at the design time, it cannot be
+known in advance exactly all the behaviours expected from the robot, as such to
+be accepted in human society robots have to learn how to interact with humans.
+Learning social interaction is a complex task, the learning will probably have
+to be made online and in the real world, as no simulator precise enough exists.
+This means that robots will have to learn directly from interacting with humans,
+which limits the quantity of datapoint possible to gather and make exploration
+riskier as actions will have real impacts on surrounding humans. Additionally,
+no clear reward function exists for social interactions. As such we argue that
+robots will highly profit from human expertise and guidance to learn social
+interactions and they also will have to make the most out of each datapoint. We
+propose to combine the Supervised Progressively Autonomous Robot Competencies
+allowing a safer online learning and Reinforcement Learning based on partial
+states rather than full states to accelerate the learning, and using more fully
+each datapoint.
 \end{abstract}
@@
 
-shaping
-guidance
+shaping \cite{knox2009interactively}
+
+guidance \cite{thomaz2008teachable}
 
@@
 
-REFORMULATE: start with size of the world and oragnisation by sensory inputs
+REFORMULATE: start with size of the world and oragnisation by sensory inputs and
+focus of attention for human, we can be aware of many things without taking them
+into account - more symbolic appraoch?
 To be usable in complex environments, a

### 2017-07-17 paper.tex
rewriting and completting first parts

--- 2017-07-13 paper.tex
@@
 \begin{abstract}
-Robots are expected to be pervasive in human society in the future
-
-not possible to hardcode everything by hand
-
-requirement for learning
-
-hard to learn for HRI
-\begin{itemize}
-	\item real time
-	\item cost of exploration (real humans)
-	\item no clear reward policy and cannot request a human to reward everything
-	\item need to make the most out of each sample
-\end{itemize}
-
-Partial state RL - accelerate learning
-
+As robots will integrate human society, they will have to satify humans'
+expectations. However at the design time, it seems hardly possible to
+know in advance exactly all the behaviours expected from the robot. As such to
+be accepted in human society robots have to learn how to interact with humans.
+But learning social interaction is a complex task. Firstly, no simulator of
+human interactions precise enough exists today, so the learning will probably have
+to be made online and in the real world.
+This means that robots will have to learn directly from interacting with humans,
+which limits the quantity of datapoint possible to gather and make exploration
+riskier as actions will have real impacts on humans or the robot itself. Additionally,
+no clear reward function exists for social interactions. As such we argue that
+robots will highly profit from human expertise and guidance to learn social
+interactions. And as the quantity of data is limited, they also will have to make the most out of each datapoint. We
+propose to combine the Supervised Progressively Autonomous Robot Competencies
+allowing a safer online learning and Reinforcement Learning based on partial
+states rather than full states to accelerate the learning by using more
+information form the human teacher.
 \end{abstract}
@@
 contexts. Robot are expected to behave appropriately regardless of the domain
-of interaction. However, not all behaviours can be known in advance and can be
+of interaction. However, not all behaviours can be known in advance and be
 implemented in the robot before its deployment in the real world. Similarly to
@@
 When interacting in the real world, humans face huge spaces of almost unlimited
-dimensions, and despite this complexity, adults and even more children are able
-to learn quickly, often from only a few demonstrations or examples. Humans are
-able to take the most out of every datapoint available to them. On the other
+dimensions, and despite this complexity, humans, and especially children are able
+to learn quickly, often from only a few demonstrations or examples. One of the
+ reason could be that they are able to take the most out of every datapoint available to them. 
+ On the other
 hand, recent impressive advances in Machine Learning such as Deep Learning~\cite{lecun2015deep}
@@
 
-Similarly to humans, robots interacting in the real world will have to be able
-to learn quickly. One way of achieving this fast learning is to learn from
-humans, i.e using human inputs to boostrap the learning. We argue that to be
-capable to interact in the real world with humans, robots have to be able to
-learn from different types of inputs: demonstrations, commands, rewards and 
-also autonomously.
+However, these immense labelled dataset or virtula worlds are not existent for
+social interaction. To learn how to interact with humans, robots will have to
+experiment in the real world facing real reactions from their actions. So they
+have to learn quickly while consistently exhibiting a decent behaviours.
+One way of ensuring this correct  behaviours is to use a human to supervised the
+the robot during the early phase of learning, and this human can also provide
+inputs to boostrap the learning, achieving a faster learning. This paper present
+a novel method based on human supervision, feature highlighting and partial
+state reinforcement learning to achieve this fast and safe learning.
 
@@
 agent is interacting in an environment
-providing positive or numerical reward in reaction to the agent's actions and
+providing numerical reward in reaction to the agent's actions and
 the agent learns an action policy to maximise the expected cummulative discounted
@@
 
-Classic approaches RL relies on exploring virtual environments where the agent
+Classic approaches RL generally rely on exploring virtual environments where the agent
 tries to maximise the reward. In most of the cases where RL achieves success, it
-had access to a virtual environment where the only real cost of exploring was
+had access to a virtual environment where the only real cost of exploring is
 time and energy, and the agent can interact as long as needed to gather
@@
 supervised learning from go master's games to learn a decent policy and then
-used convolutional networks, self play and tree search to achieve super-human
+used deep learning, self play and tree search to achieve super-human
 capabilities and beatting humans best players.
@@
 \subsubsection{Guiding the learning}
-Rather than providing initial knowledge to the agents, humans can also guide the
-agent throughout the learning by organising the tasks the robot will face, this
-approach is known as scaffolding \cite{saunders2006teaching}. This allows to
-teach the robot successive more complex policies by increasing the complexity of
-the task presented and reusing previously learnt behaviours.
+Rather than solely providing initial knowledge to the agents, humans can also guide the
+agent throughout the learning in a more human-like teaching scenario.
 
-shaping
-guidance
+A first possibility is organising the tasks the robot will face. 
+This approach, known as scaffolding \cite{saunders2006teaching} progressively
+increase the difficulty and complexity of the task or the environment as the
+robot is learning to achieved complex policy not directly learnable in the final
+environment.
+
+Another possibility is shaping. For example, the TAMER framework
+\cite{knox2009interactively}, allows to teach an agent an action policy in an
+environment providing no rewards using a human observer to supply rewards to the
+agent. One of the interest of this approach is that the teacher can adapt the
+rewards to the current policy of the agent, for example starting to reward
+positively suboptimal behaviours but which still improve the current policy and
+later, as the agent improve its behaviour reward these same suboptimal behaviour
+negatively and only the optimal ones positively.
+
+A last possibility to guide the the learning is to bias the action selction.
+In~\cite{thomaz2008teachable}, the authors propose to use a human supervisor to
+supply  an agent both rewards and potential guidance or advise indicating where
+the agent should pay attention, or what it should do next. And they show that
+giving the power to the supervisor to bias the action selection can improve the
+learning, making it faster, safer.
 
@@
 interacting with its environment, we proposed the Supervised Progressively
-Autonomous Robot Competencies (SPARC) in \cite{senft2015sparc}. SPARC is independent
-of the learning algorithm used, but define an interaction dynamic between an
-agent learning an action policy while interacting in an environment and a
-supervisor teaching this agent an action policy. The main goal of SPARC is
+Autonomous Robot Competencies (SPARC) in~\cite{senft2015sparc}. SPARC defines an
+interaction dynamic between an agent learning an action policy while interacting
+in an environment and a
+supervisor teaching this agent what to do. The main goal of SPARC is
 enabling a robot to learn from a supervisor while ensuring that every action
@@
 action and combine this with online learning on the agent side. This control is
-achieved using a suggestion/correction mechanism whereas the agent is presenting
+achieved using a suggestion/correction mechanism whereby the agent presents
 to the supervisor the action about to be executed and the supervisor can cancel
@@
 executed after a delay. Additionally, the supervisor can select actions to be
-executed by the agent. The actions selected or canceled by the supervisor can be
+executed by the agent. The actions selected, accepted or canceled by the supervisor can be
 used as input with the current state by a learning algorithm to progressively
-improve the future suggestions.
+improve the future suggestions thus reducing the reliance on the supervisors.
 
@@
 execution can ensure that even in the early phases of the learning the agent can
-have an appropriate action policy for the current environment as shown in Figure~\ref{fig:comparison}.
+have an appropriate action policy for the current environment as shown in
+Figure~\ref{fig:comparison} while making the learning faster compared to
+autonomous learning. (update figure with autonomous learning, classical learning from human rewards
+and sparc)
 
@@
     \includegraphics[width=0.9\linewidth]{./fig/motivation.pdf}
-    \caption{Idealised expectation for performance, autonomy and workload for a
-    Wizard of Oz, a autonomous learner and SPARC.}
+    \caption{Idealised expectation for performance, autonomy and human workload for a
+    an autonomous learner, an approach using human rewards and SPARC.}
     \label{fig:comparison}
@@
 SPARC has been design with the idea of teaching a robot to interact with humans,
-it is specially usefull when the pace of action selection is low (less than
-1Hz), when the agent has to learn with a limited number of datapoints and when
-undesired actions executed by an agent can have a high cost.
+it is specially usefull when the frequency of action selection is low (less than
+1Hz) so action can be evaluated by a human before being executed, when the agent
+has to learn with a limited number of datapoints and when
+undesired actions executed by an agent can have a high cost and are to be
+avoided.
 
@@
 was not making use of any type of generalisation, it was directly mapping a
-single state action pair to a reward, and as such has limited efficiency in
-environments with a continuous space or a high dimensional and undeterministic
-one.
+single state action pair to a reward, and as such had limited efficiency in
+environments with a continuous or high dimensional space or undeterministic
+transition from one state to another.
 

### 2017-07-17 paper.tex
update

@@
 
-REFORMULATE: start with size of the world and oragnisation by sensory inputs and
-focus of attention for human, we can be aware of many things without taking them
-into account - more symbolic appraoch?
-To be usable in complex environments, a
-learning algorithm requires generalisation as exactly identical spaces might
-never been observed twice in the life time of the agent.
+Humans evolve in a highly complex environment with a nearly infinite number of
+dimensions originating from different modality through our senses. But, despite
+this complexity, we can select actions according to important features of the
+state, regardless of other parts of it.
 
-A classical approach to generalise in RL is to use a first layer of neural
-network or to use deep reinforcement learning which relies on deep neural
-networks to learn a mapping state action Qvalue for example. (ADDREF)
-These approaches, neural network based, relies on having a large number of
-datapoints to converge toward a good function approximator. However, as
-discussed previously, in many application, these amounts of data are not
-possible to be obtained and a robot might need to adapt to different persons and
-be retrained quickly.
+Taking inspiration from this observation, we argue that focusing on partial states, rather
+than full states can both increase the speed of learning for an agent and
+provide some of the generalisation required to interact in complex environment.
+Guidance from a human can highlight important features in the state space and
+associate them to actions. This shifts the state action pair paradigm to a
+partial-state action pair, and in the case of RL, the tuple: partial-state,
+action and reward.
 
-With that idea in mind, we propose to make a better use of human inputs, and ask
-the supervisor to identify which features of the environment are linked to the
-current selected action. Instead of having an state-action pair, we
-can have a partial-state action pair, with this partial-state being a subset of
-the state domain.
+%A classical approach to generalise in RL is to use a first layer of neural
+%network or to use deep reinforcement learning which relies on deep neural
+%networks to learn a mapping state action Qvalue for example. (ADDREF)
+%These approaches, neural network based, relies on having a large number of
+%datapoints to converge toward a good function approximator. However, as
+%discussed previously, in many application, these amounts of data are not
+%possible to be obtained and a robot might need to adapt to different persons and
+%be retrained quickly.
+
+%With that idea in mind, we propose to make a better use of human inputs, and ask
+%the supervisor to identify which features of the environment are linked to the
+%current selected action.
 
@@
 \subsection{Supervisation}
-Similarly to a SPARC setup, the supervisor is presented with action about to be
-executed by the robot and can either cancel it or let it be executed and the 
-supervisor has the possibility to select actions for the robot to execute.
+Similarly to a SPARC setup, the supervisor can select actions, or when presented
+with an action about to be executed by the robot either cancel it or let
+it be executed.
 
 In addition to these actions, the supervisor can use the GUI to select features
-of the environment that can send to the algorithm to reduce the state associated
+of the environment that can be sent to the algorithm to reduce the state associated
 to this action to a partial-state. Similarly, the algorithm can indicate which
@@
 
-Example?
+%Example?
 
@@
 expected future impacts of an action removes the problem of credit assignment
-for delayed rewards and allows us to consider only a myopic approach. (can cite
-kobers I think.)
+for delayed rewards and allows us to consider only a myopic approach.
 
@@
 number $n' \leq n$ of the dimensions of S). For example, a state s could be
-defined in 4 dimensions such as $s=[1,0.2,0,0.5]$, and s' in two dimensions with
-$s'=[-,0.2,0,-]$ with symbol '-' reprensenting the dimensions removed.
+defined in 4 dimensions such as ${s=[1,0.2,0,0.5]}$, and s' in two dimensions with
+${s'=[-,0.2,0,-]}$ with symbol '$-$' reprensenting the dimensions removed.
 
-We store in memory the partial-state action pair $s'-a_{i}$, with the reward 1
+We store in memory the partial-state action pair $s'$-$a_{i}$, with the reward 1
 as the action has been selected by the supervisor. Similarly, if an action has
-been canceled by the supervisor, the partial-state action will be assigned to a
-reward $-1$.
+been canceled by the supervisor, the partial-state action pair will be assigned to a
+reward -1.
 
 After interacting with the system under the supervisors control, the actions
-will have associated to each action $a \in A$, a collection $C_{a}$ of pairs
-partial-state-reward. When facing a new state $s$ where an action has to be
+will have associated to each action ${a \in A}$, a collection $C_{a}$ of pairs
+partial-state reward. When facing a new state $s$ where an action has to be
 selected, the agent can select an action following Algorithm \ref{algo}.
@@
             compute similarity
-            $\Delta(s',s)=1-\frac{\sum_{j}^{n'}(s'(j)-s(j))^{2}}{n'}$
+            $\Delta(s',s)=1-\frac{\sum_{i}^{n'}(s'(i)-s(i))^{2}}{n'}$
         }
@@
 \end{algorithm}
+In case of mutiple states s' with different rewards, only the most recent one
+can be stored in memory, allowing a supervisor to correct potential errors, or
+adapt to change of desired policy.
 
 When proposing an action following Algorithm~\ref{algo}, the agent can also use
-the dimensions of the similar state s' to indicate the supervisor which parts of
-the states have been used for the action selection.
+the dimensions of the similar state s' used for the selection to indicate the
+supervisor which parts of the state have been used for the action selection.
 
@@
 
-The main challenge for using Interactive Machine Learning is to translate the
-state-action space between the human view and the algorithm view. This is one
-important reason why many researchers in IML focuse on limiting the human impact
+Check Power to people and use it as bases for challenge discussion.
+
+One important challenge for using Interactive Machine Learning is to translate the
+state-action space between the human view and the algorithm view. This is a
+reason why many researchers in IML focuse on limiting the human impact
 to providing reward~\cite{knox2009interactively} or kinesthetic demonstrations
@@
 as guidance biasing the action selection can lead to a better performance in the
-learning. But to able to use these higher level and more complex inputs from
+learning. However, to able to use these higher level and more complex inputs from
 humans, these actions have to be translated in inputs usable for the learning

### 2017-07-18 paper.tex
Rework challenges

@@
 
-Check Power to people and use it as bases for challenge discussion.
+A large body of the
+Interactive Machine Learning research is focused on simple inputs from the
+humans, such as providing labels \cite{cakmak2012designing}, rewards
+\cite{knox2009interactively} or kinesthetic demonstrations
+\cite{billard2008robot}. However, as stated in \cite{amershi2014power}: "people
+want to demonstrate how learners should behave" and "users may desire richer
+control over machine-learning systems than simply labeling data". Human teachers
+want to be more active and involved in the teaching process, to make their
+student learning faster. 
+And, as shown in \cite{senft2017supervised}, providing teacher with this control
+can keep the agent in relevant states of the environment, speeding the learning
+and reducing the risk to have the robot execute undesired actions.
 
-One important challenge for using Interactive Machine Learning is to translate the
-state-action space between the human view and the algorithm view. This is a
-reason why many researchers in IML focuse on limiting the human impact
-to providing reward~\cite{knox2009interactively} or kinesthetic demonstrations
-in the robot space~\cite{billard2008robot}. However as shown by Thomaz and Breazeal~\cite{thomaz2008teachable}, using more complex inputs from the supervisor, such
-as guidance biasing the action selection can lead to a better performance in the
-learning. However, to able to use these higher level and more complex inputs from
-humans, these actions have to be translated in inputs usable for the learning
-algorithm and/or the action selection mechanism.
-
-The more complex the inputs from the humans are the more additional information
-can be transmitted to the learning, allowing the agent to learn more complex
-behaviours faster.
-
-Similarly, as shown by Senft and al. in \cite{senft2017supervised}, providing
-more control to the supervisor about the robot actions can lead to keep the
-agent in relevant states of the environment and as such speeding the learning
-and making it safer for the robot and people interacting with it. However this
-method is dependent of letting the human know what action the robot is about to
-execute, which relies on the robot to express its intention in a human
-understandable way. (ADDREF - see Serge?)
-
-Another challenge is state representation, the state accessed by the learning
-algorithm and the one accessed by the supervisor can be represented is highly
-different space, covering different features, and if the robot aims to profit
-from the human initial knowledge, it needs to have access to similar features in
-the environment to the ones the human is using, and the human needs to be able
-to transmit these features to the learning algorithm.
-(the representation of the state is often engineered by the programmers of the
-algorithm, and space features not considered in the initial design could
-actually be important in the final one. Idea of Deep Learning, but not enough
-datapoints.)
-
-Needs a parallel to human learning from humans
+In human social learning, both interactants have access to a similar set of
+inputs: the senses available to a human body, and the teacher has additional
+knowledge about the environment that can be communicated in an open ended way to
+the learner. On the other in human-robot teaching, the way to sense the world
+can be highly different between the two partners, and as of today, there is no
+open ended way of communicating new concepts or explication as natural langage
+processing is not yet solve. This creates two main challenges to make robot
+learning for human use complex inputs: 
+\begin{itemize}
+    \item Having a mapping between the action state space of the human and the
+            robot ensuring that feature used for action selection for one
+            interactant are available to the other.
+    \item Communicating these features from one participant to the other: allow
+        the robot to make sense of the human's instructions and the human to
+        understand the robot's intentions.
+\end{itemize}
 

### 2017-07-18 paper.tex
End of first pass

@@
 
-Other way of extending the current work would be to combine it with the
-possibility of letting the agent continue to explore in the absence of a
-supervisor around a learnt action policy to keep improving its behaviour. This
+The current work could be extended to allow the agent continue to improve its
+behaviour even in the absence of supervisor, exploring around a learnt policy
+progressively improving its policy beyond what have been taught. This
 could be done by allowing the supervisor to provide rewards during the learning
-phase, rewards which could also be assigned to partial states. The system could
-also learn to predict these rewards in an approach similar to TAMER 
-\cite{knox2009interactively}. But in the case of an absence of supervisor, the assumption that only a
+phase, and combine these rewards with the demonstrations to learn a reward
+function in a fashion similar to Inverse Reinforcement Learning
+\cite{abbeel2004apprenticeship}. These could also use partial states associated
+to these rewards to have a general reward function despite a low number of
+datapoints.
+But without the supervisor, the assumption that only a
 myopic action selection is sufficient would not hold anymore and the problem of
-delayed rewards would have to be tackled. It could be for example possible to
-adapt well known algorithms such as QLearning to handle partial states rather
-the full states.
-
+delayed rewards would have to be tackled.
 %===============================================================================

### 2017-07-20 paper.tex
Half updates after Sev's comments

@@
 \usepackage[ruled,vlined]{algorithm2e}
+\usepackage{comment}
+\usepackage{amssymb}
 \frenchspacing  %Required
@@
 \author{Emmanuel Senft \\
-CNRS \\
+CRNS \\
 Plymouth University \\
@@
 \And S\'{e}verin Lemaignan\\
-CNRS \\
+CRNS \\
 Plymouth University \\
@@
  \And Tony Belpaeme\\
- CNRS\\ Plymouth University (UK) \\ iMinds \\ Ghent University (Be)}
+ CRNS\\ Plymouth University (UK) \\ iMinds \\ Ghent University (Be)}
 
@@
 \begin{abstract}
-As robots will integrate human society, they will have to satify humans'
-expectations. However at the design time, it seems hardly possible to
-know in advance exactly all the behaviours expected from the robot. As such to
-be accepted in human society robots have to learn how to interact with humans.
-But learning social interaction is a complex task. Firstly, no simulator of
-human interactions precise enough exists today, so the learning will probably have
+%As robots will integrate human society, they will have to satify humans'
+%expectations. However at the design time, it seems hardly possible to
+%know in advance exactly all the behaviours expected from the robot. As such to
+%be accepted in human society robots have to learn how to interact with humans.
+Learning social interaction is a complex task. Firstly, no simulator of
+human interactions sufficiently precise exists today, so the learning will probably have
 to be made online and in the real world.
@@
 
+For a robot, interacting in the real world requires to combine inputs
+ from many sensors to create a space composed of large number dimensions and
+select actions appropriated to the current space. However,
+ parts of the state can be irrelevant to the current goal and are not required
+ to be taken into account to select the current action. A successful action
+ policy maps these features to the relevant actions.
+
+These relevant features in the space can be encoded in the representation of
+the space the robot uses for action selection or be learnt. Recent successes in Deep
+Learning~\cite{lecun2015deep} have shown that complex features can be extracted
+by neural networks assuming that enough datapoints are available.
+
+In previous work~\cite{senft2015sparc,senft2017supervised}, we introduced the
+Supervised Progressively Autonomous Robot Competencies (SPARC), as a way to
+teach a robot an action policy while interacting based on a supervisor
+correcting actions about to be executed by the robot. In this paper, we propose
+to extend this approach to allow the supervisor to highlight features in the
+environment associated to the selected action. During the action selection
+phase, the robot can compare these features, defined as partial states, with the
+current state to select an action based on which previously identify
+features are currently in the environment.
+
+\begin{comment}
+This approach in especially relevant for HRI as gathering datapoints has to be
+performed in the real world and interacting with humans forces a robot to have
+an appropriate action policy at anytime of the interaction. even in the early
+phase when the robot has no information about the way its environment react to
+its actions.
+
 When interacting in the real world, humans face huge spaces of almost unlimited
@@
 
-However, these immense labelled dataset or virtula worlds are not existent for
-social interaction. To learn how to interact with humans, robots will have to
-experiment in the real world facing real reactions from their actions. So they
-have to learn quickly while consistently exhibiting a decent behaviours.
-One way of ensuring this correct  behaviours is to use a human to supervised the
+However, these large labelled dataset or virtul worlds do not exist for
+social interaction. To learn how to interact with humans, robots have to
+experiment in the real world facing the actual reactions from their actions. As
+such they
+have to learn quickly while consistently exhibiting a acceptable behaviours.
+One way of ensuring this correct  behaviours is to rely on a human to supervise
 the robot during the early phase of learning, and this human can also provide
@@
 state reinforcement learning to achieve this fast and safe learning.
-
+\end{comment}
 %===============================================================================
@@
 
-The main framework to provide a robot with autonomous learning is Reinforcement
+The main framework for an agent to learn how to interact in an environment while
+interacting is Reinforcement 
 Learning (RL)~\cite{kober2013reinforcement,sutton1998reinforcement}. In RL, an
@@
 
-Classic approaches RL generally rely on exploring virtual environments where the agent
-tries to maximise the reward. In most of the cases where RL achieves success, it
-had access to a virtual environment where the only real cost of exploring is
+Classic approaches in RL generally rely on exploring virtual environments where the agent
+tries to maximise the reward. In many cases where RL achieves success, the agent
+had access to a virtual environment where the only real cost of exploring was 
 time and energy, and the agent can interact as long as needed to gather
@@
 these conditions are reunited, RL can achieve impressive results, as shown by
-the victory of a computer in Backgammon back in the 90s~\cite{tesauro1995temporal} or more recently the success achieved in playing
+the victory of a computer in Backgammon back in the
+90s~\cite{tesauro1995temporal} or more recently the success achieved in playing
 Atari games based only on the image and the game rewards~\cite{mnih2015human}.
 
-\subsection{Human enhanced Reinforcement Learning}
+\subsection{Human impact on Reinforcement Learning}
 
-No simulator of world, and especially of social interactions allows robots to 
-learn in a virtual environment, so robots, especially if the have to interact
-with humans have to be able to learn in the real world.
-However, in the real physical world, every actions have an impact on the
-environment, especially in HRI when actions can upset and negatively impact
-humans interacting with the robot. Additionally acquiring datapoints in can be
-expensive in term of time and other ressources. As such many approaches aiming
-at providing robot with learn to interact in the real world have relied on
-knowledge provided by a human in different way to avoid this random exploration
-presenting risk to the robot and persons interacting with it.
+Initial knowledge is often a crucial step to allow an algorithm to learn an
+efficient action policy. This knowledge, originating from human expertise, can
+be exploited in many ways.
 
-\subsubsection{Initial knowledge}
-One way to use human knowledge to help an agent to learn is through providing
-initial knowledge. By providing demonstrations of an expected actions policy,
-humans can boostrap the learning and provide the agent with a more appropriate
-action policy that it can improve over time.
+\subsubsection{Design decisions:}
+Initial knowledge has to be use in the designing of the algorithm, the
+representation of the state and actions spaces and the rewrd funtion. For
+example, only carefully crafted features allowed
+Tesauro to improve its algorithm for Backgammon from a intermediate-level player
+to super-human level~\cite{tesauro1995temporal}. Similarly, the design of
+complex neural networks for state generalisation, the representation of actions
+as motor primitive rather than raw motor angles or adding additional
+informations in the reward function have important impacts on the ability of
+the robot to reach a successful policy.
 
-These demonstrations can be used to create an initial action policy which could
-have been discovered autonomously, but without requiring an initial discovery
-phase where the performance has to be low when the agent is learning from its
-environment. Recent work~\cite{hester2017learning} have shown that using initial
-human demonstrations can allow the initial performance to be much better than
-starting from scratch in playing Atari games, and even sometimes this allow to
-achieve higher performance than only relying on exploration to learn an action
-policy.
-
-In some cases, the state space is too big to rely only on random exploration to
-reach a successful action policy. For example the game of Go in its larger board
-size contains more than $10^{210}$ states, so exhaustive search is not possible
-with today's ressources. Authors of \cite{silver2016mastering} started with
+\subsubsection{Demonstrations:}
+Initial knowledge can be provided to the agent learning through demonstrations.
+These demonstrations can be used to create an initial policy sufficiently
+efficient to start interacting in the environment and gather information to
+improve over time. This initial policy, required to receive meaningful feedback
+from the environment can be impossible to reach by relying only on random
+exploration and feedback from the environment. For example the game of Go in its larger board
+size contains more than $10^{210}$ states, so exhaustive search is not possible.
+Authors of \cite{silver2016mastering} started with
 supervised learning from go master's games to learn a decent policy and then
 used deep learning, self play and tree search to achieve super-human
-capabilities and beatting humans best players.
+capabilities and beating humans best players.
 
-Another way to use these demonstrations is Inverse
-Reinforcement Learning, the agent derives from demonstrations of an expert an
-expected reward function that it can use to improve a policy based on the
-demonstrations and so achieving higher performance than the demonstrations
-themselves. By using this technic, Abbeel managed to teach an autonomous
-helicopter to do high level acrobatics often only executable by high level
-expert~\cite{abbeel2004apprenticeship}.
+These demonstrations can also be used to learn a reward function. With Inverse
+Reinforcement Learning, the agent is not provided with a reward function, but
+derives it from a set of expert demonstrations. The agent can then explore
+around the demonstrated policy to find how to optimise the reward function. With
+this approach, Abbeel and Ng achieved better than human control for a robotic
+helicopter~\cite{abbeel2004apprenticeship}.
 
-%One of the main challenge when applying RL to robotics is poor perfermance in
-%the early stages of the learning as the agent has to explore the environment to
-%gather initial knowledge. This challenge is especially
-%important for robotics as trials often have to happen in the real world (as
-%simulator close enough to the real world as not available) and as such can
-%present risks for the robot or for the persons interacting with it.
+\subsubsection{Guiding the learning:}
 
-\subsubsection{Guiding the learning}
-Rather than solely providing initial knowledge to the agents, humans can also guide the
-agent throughout the learning in a more human-like teaching scenario.
+In some cases, the state space is simply too big to rely only on random exploration to
+reach a successful action policy.Rather than solely providing initial knowledge
+to the agents, humans can also guide the agent throughout the learning in a more
+human-like teaching manner.
 
-A first possibility is organising the tasks the robot will face. 
-This approach, known as scaffolding \cite{saunders2006teaching} progressively
+A first approach consists in sequencing tasks the robot will face. 
+This approach, known as "scaffolding" \cite{saunders2006teaching}, progressively
 increase the difficulty and complexity of the task or the environment as the
-robot is learning to achieved complex policy not directly learnable in the final
+robot is learning policies to achieve complex task not directly learnable in the final
 environment.
 
-Another possibility is shaping. For example, the TAMER framework
+A second approach is "shaping". For example, the TAMER framework
 \cite{knox2009interactively}, allows to teach an agent an action policy in an
 environment providing no rewards using a human observer to supply rewards to the
-agent. One of the interest of this approach is that the teacher can adapt the
-rewards to the current policy of the agent, for example starting to reward
+agent. With this approach the teacher can adapt the
+rewards to the current policy and performance of the agent, for example starting to reward
 positively suboptimal behaviours but which still improve the current policy and
@@
 
-A last possibility to guide the the learning is to bias the action selction.
+Another approach to guide the the learning is to bias the action selection.
 In~\cite{thomaz2008teachable}, the authors propose to use a human supervisor to
@@
 
-%===============================================================================
+In \cite{senft2015sparc}, we introduced the Supervised Progressively
+Autonomous Robot Competencies (SPARC). SPARC relies on the presence of a
+supervisor teaching a robot how to interact in an environment. This teacher
+knowns which actions the robot is about to execute and can cancel an action or
+select another to be executed. Based on the supervisor's decisions, the robot
+learns which actions are desired and can refine its policy over time reducing
+the need for the teacher to correct or select an action.
 
-\section{Proposition}
-\subsection{Supervised Progressively Autonomous Robot Competencies}
-
-As a way to enable a human supervisor to teach a robot an action policy while
-interacting with its environment, we proposed the Supervised Progressively
-Autonomous Robot Competencies (SPARC) in~\cite{senft2015sparc}. SPARC defines an
-interaction dynamic between an agent learning an action policy while interacting
-in an environment and a
-supervisor teaching this agent what to do. The main goal of SPARC is
-enabling a robot to learn from a supervisor while ensuring that every action
-executed by the robot has approval of the supervisor but without requiring this
-supervisor to manually enforce every single action.
-
-The main concept in SPARC is giving the supervisor the control over the agent
-action and combine this with online learning on the agent side. This control is
-achieved using a suggestion/correction mechanism whereby the agent presents
-to the supervisor the action about to be executed and the supervisor can cancel
-this action before its execution or not doing anything, letting the action being
-executed after a delay. Additionally, the supervisor can select actions to be
-executed by the agent. The actions selected, accepted or canceled by the supervisor can be
-used as input with the current state by a learning algorithm to progressively
-improve the future suggestions thus reducing the reliance on the supervisors.
-
-Giving power to an expert to correct the actions of the agent before the
-execution can ensure that even in the early phases of the learning the agent can
-have an appropriate action policy for the current environment as shown in
-Figure~\ref{fig:comparison} while making the learning faster compared to
-autonomous learning. (update figure with autonomous learning, classical learning from human rewards
-and sparc)
+SPARC gives control on the robot actions to an expert, who can guide the
+exploration in the desired part of the environment and this ensures the robot's
+behaviour is consistently appropriate. As the exploration is
+guided, and all the actions are useful, the learning can be faster than
+autonomous learning or feedback based learning as illustrated in Figure
+\ref{fig:comparison}.
 
@@
 
-SPARC has been design with the idea of teaching a robot to interact with humans,
-it is specially usefull when the frequency of action selection is low (less than
-1Hz) so action can be evaluated by a human before being executed, when the agent
-has to learn with a limited number of datapoints and when
-undesired actions executed by an agent can have a high cost and are to be
-avoided.
+%SPARC has been designed with the idea of teaching a robot to interact with humans,
+%it is specially usefull when the frequency of action selection is low (less than
+%1Hz) so action can be evaluated by a human before being executed, when the agent
+%has to learn with a limited number of datapoints and when
+%undesired actions executed by an agent can have a high cost and are to be
+%avoided.
 
@@
 assigning a positive reward to every action executed by the robot as it would
-have been passively or actvely validated by the supervisor. However this method
-was not making use of any type of generalisation, it was directly mapping a
-single state action pair to a reward, and as such had limited efficiency in
+have been explicitely or implicitely approved by the supervisor. However this method
+was not making use of any kind of generalisation, directly mapping a
+single (state,action) pair to a reward, and as such is not applicable to
 environments with a continuous or high dimensional space or undeterministic
@@
 
-\subsection{Partial-State Supervised Reinforcement Learning}
-
+\section{Partial-State Supervised Reinforcement Learning}
+\begin{comment}
 Humans evolve in a highly complex environment with a nearly infinite number of
@@
 action and reward. 
+\end{comment}
 
-%A classical approach to generalise in RL is to use a first layer of neural
-%network or to use deep reinforcement learning which relies on deep neural
-%networks to learn a mapping state action Qvalue for example. (ADDREF)
-%These approaches, neural network based, relies on having a large number of
-%datapoints to converge toward a good function approximator. However, as
-%discussed previously, in many application, these amounts of data are not
-%possible to be obtained and a robot might need to adapt to different persons and
-%be retrained quickly.
+To make RL applicable in high dimensional or continuous states, the algorithm
+requires a way to generalise knowledge to unseen states. 
+A classical approach is to use a first layer of neural
+network or to use deep reinforcement learning which relies on deep neural
+networks to learn a mapping state action Qvalue for example. 
+These approaches, neural network based, relies on having a large number of
+datapoints to converge toward a good function approximator. However, as
+discussed previously, in many application, these amounts of data are not
+possible to be obtained and methods to generalise quickly are more desirable.
 
-%With that idea in mind, we propose to make a better use of human inputs, and ask
-%the supervisor to identify which features of the environment are linked to the
-%current selected action.
+%In \cite{sutton1996generalisation}, Sutton proposed to use sparse coarse
+%coding
+%dividing the state in slices and tiles as a way to generalise quickly for
+%continuous spaces in RL.
 
+In this paper we propose to use a human to highlight the relevant features of
+the environment to reduce the state dimension of the points stored in memory.
+We introduce the concept of partial-state, a sliced version of the state defined
+only on a subset of the dimensions of the state. This shifts the (state,action)
+pair paradigm to (partial-state,action)  
+and in the case of RL, the tuple (state, action, reward) to (partial-state,
+action, reward).
+
+\begin{comment}
 %===============================================================================
@@
 
-\subsection{Supervisation}
 Similarly to a SPARC setup, the supervisor can select actions, or when presented
@@
 %Example?
+\end{comment}
 
@@
 
-In a first approach, the presence of an expert supervisor who can evaluate the
-expected future impacts of an action removes the problem of credit assignment
-for delayed rewards and allows us to consider only a myopic approach.
+An expert supervises the agent actions, and can assign rewards to actions and
+highlight the part of the states which are relevant to assigning this reward to
+this partial-state.
+
+As the supervisor can estimate the future impacts of an action, the problem of
+credit assignment for delayed rewards can be ignored  and allows us to consider
+only a myopic approach.
 
 For this paper, we will reuse the formalism of rewardless Markov Decision 
-Process to identify the different elements of our system. The agent has action
-to a set of actions A, a state S (represented as a vector of n dimensions of
-values $\in [0;1]$). With each dimension of S representing features in the
-environment.
+Process to identify the different elements of our system. The agent has access
+to a set of actions $\mathcal{A}$, a state $\mathcal{S} \in [0,1]^{n}$. We
+also define the partial-states $\mathcal{s'} \in [0,1]^{n'}$ with $n' \leq n$ as a
+slice of $\mathcal{S}$, a subset of $\mathcal{S}$ where some dimensions have
+been removed. 
+%With each dimension of S representing features in the environment.
 
-At the state $s_{t}$ the agent receives the action $a_{i}$ with the partial
-state $s'$ defined in a subspace $S' \subseteq S$ (defined by selecting only a
-number $n' \leq n$ of the dimensions of S). For example, a state s could be
-defined in 4 dimensions such as ${s=[1,0.2,0,0.5]}$, and s' in two dimensions with
-${s'=[-,0.2,0,-]}$ with symbol '$-$' reprensenting the dimensions removed.
+At the instant $t$, the agent has access the state $s$, an action $a$, evaluated
+with a reward $r$ associated to the partial-state $s'$. For example, a state $s$ could be
+defined in 4 dimensions such as ${s=[1,0.2,0,0.5]}$, and $s'$ in two dimensions with
+${s'=[-,0.2,0,-]}$ with symbol '$-$' reprensenting the dimensions removed. The
+action $a$ has been evaluated $r$ in the partial-state $s'$.
 
-We store in memory the partial-state action pair $s'$-$a_{i}$, with the reward 1
-as the action has been selected by the supervisor. Similarly, if an action has
-been canceled by the supervisor, the partial-state action pair will be assigned to a
-reward -1.
+To each action
+$a \in \mathcal{A}$ we can associate a set $\mathcal{C}_{a}$ of pairs $(s',r)$
+representing the rating done by the supervisor to action $a$ with feature
+highlighted for $s'$. When adding a new pairt $(s',r)$, we can discard all the
+previous pairs with an identical $s'$ to represent the evolution of the policy
+evaluation by the supervisor.
 
-After interacting with the system under the supervisors control, the actions
-will have associated to each action ${a \in A}$, a collection $C_{a}$ of pairs
-partial-state reward. When facing a new state $s$ where an action has to be
-selected, the agent can select an action following Algorithm \ref{algo}.
+When facing a new state $s$ where an action has to be
+selected, the agent can select an action following Algorithm~\ref{algo}. For
+each action $a \in \mathcal{A}$, we take the pair $(s',r)$ with the closest $s'$
+to the current state (as defined by normalised distance over the dimensions
+where $s'$ is defined). That way, each action $a$ can be associated to an
+expected reward defined by the product between the similarity of the closest
+partial-state known for $a$ and the reward obtained in that partial-state.
+Finally, the action with the highest expected reward can be selected.
 
@@
     \SetKwInOut{Input}{inputs}\SetKwInOut{Output}{output}
-    \Input{Current state s, action-partial state rewards tuples}
+    \Input{Current state $s$, set of  $(a,s',r)$}
     \Output{selected action $\pi(s)$}
-    \ForEach{a $\in$ A}{
-        \ForEach{s'-r $\in C_{a}$}{
-            compute similarity
-            $\Delta(s',s)=1-\frac{\sum_{i}^{n'}(s'(i)-s(i))^{2}}{n'}$
+    \ForEach{$a \in \mathcal{A}$}{
+        \ForEach{$(s'-r) \in \mathcal{C}_{a}$}{
+            compute similarity $\Delta$ between $s$ and $s'$:
+            $\Delta(s')=1-\frac{\sum_{i}^{n'}(s'(i)-s(i))^{2}}{n'}$
         }
-        $\Delta(a)=max(\Delta)$
-
-        $r(a)=R(argmax_{s'} \Delta(s'))$
+        compute expected reward $\hat{r}(a)$:
+        $\hat{r}(a) = max(\Delta) \cdot r(arg\, max_{s'} \Delta(s'))$\\
+        with $r(\Delta(s'))$ reward of $(s'-r)$ pair
     }
-    $\pi(s) = argmax_{a}\Delta(a) \cdot r(a)$
+    $\pi(s) = arg\, max_{a} \hat{r}(a)$
 
@@
 \end{algorithm}
-In case of mutiple states s' with different rewards, only the most recent one
-can be stored in memory, allowing a supervisor to correct potential errors, or
-adapt to change of desired policy.
 
-When proposing an action following Algorithm~\ref{algo}, the agent can also use
-the dimensions of the similar state s' used for the selection to indicate the
+When selecting an action with following Algorithm~\ref{algo}, the agent can also use
+the dimensions of the similar state $s'$ used for the selection to indicate the
 supervisor which parts of the state have been used for the action selection.
 
+\subsection{Combination with SPARC}
+
+SPARC has been showed to be compatible with RL in \cite{senft2017supervised},
+and can also be easily combined with the approach presented in paper using
+partial states. For example, when selecting an action for the robot to be
+executed, the supervisor can also select which features in the environment
+should be selected in the partial state, and this associate the reward +1
+to this action in this partial state. Similarly when an action is
+proposed
+to the supervisor the dimensions features represented by the dimensions of the
+closest partial state can be explosed to the supervisor as a way to explain why
+this action has been selected. Facing this, the supervisor can not react,
+letting the action being executed and associating a reward of +1 to the partial
+state and the action proposed, the supervisor could also change the partial
+state to correct the features related to this action or cancel it, preventing the
+execution and associating a reward of -1.
+
+\section{Example of application}
 %===============================================================================
+\begin{comment}
 \section{Challenges}
@@
 \end{itemize}
-
+\end{comment}
 \section{Future work}
@@
 The current work could be extended to allow the agent continue to improve its
-behaviour even in the absence of supervisor, exploring around a learnt policy
-progressively improving its policy beyond what have been taught. This
+behaviour even in the absence of supervisor, progressively exploring around a learnt policy
+improving its policy beyond what have been taught. This
 could be done by allowing the supervisor to provide rewards during the learning
@@
 %===============================================================================
-\section{Conclusion}
+%\section{Conclusion}
 \label{sec:conclusion}

### 2017-07-21 paper.tex
Add an example part

@@
 \usepackage{amssymb}
+\usepackage{subcaption}
 \frenchspacing  %Required
@@
 
-When facing a new state $s$ where an action has to be
-selected, the agent can select an action following Algorithm~\ref{algo}. For
-each action $a \in \mathcal{A}$, we take the pair $(s',r)$ with the closest $s'$
-to the current state (as defined by normalised distance over the dimensions
-where $s'$ is defined). That way, each action $a$ can be associated to an
-expected reward defined by the product between the similarity of the closest
-partial-state known for $a$ and the reward obtained in that partial-state.
-Finally, the action with the highest expected reward can be selected.
-
 \begin{algorithm}
@@
 \end{algorithm}
+
+When facing a new state $s$ where an action has to be
+selected, the agent can select an action following Algorithm~\ref{algo}. For
+each action $a \in \mathcal{A}$, we take the pair $(s',r)$ with the closest $s'$
+to the current state (as defined by normalised distance over the dimensions
+where $s'$ is defined). That way, each action $a$ can be associated to an
+expected reward defined by the product between the similarity of the closest
+partial-state known for $a$ and the reward obtained in that partial-state.
+Finally, the action with the highest expected reward can be selected.
 
@@
 \section{Example of application}
+
+An example of application yet to be tested is robot for teaching to children.
+A robot can play an educative game with children to teach them notions about
+diverse topics according to the needs of the teacher. For this example, a child
+and a robot are playing a game about food web, teaching wich animals eat which
+ones on a Sandtray~\cite{baxter2012touchscreen} as shown in
+Figure~\ref{fig:game}. In addition to the child and
+the robot, an adult supervises the robot using a tablet with a Graphical User
+Interface (GUI) (Figure~\ref{fig:gui}) to teach the robot how to interact with the child.
+\begin{figure}
+        \centering
+  \includegraphics[width=80mm]{./fig/game.png} 
+    \caption{Game displayed on the Sandtray the child is playing with the robot.}
+        \label{fig:game}
+\end{figure}
+
+As shown in Figures \ref{fig:game} and \ref{fig:gui}, the GUI is an augmented
+version of the game itself, which can be use to make the robot move items on the
+game by dragging them on the GUI or which can display actions proposed by the
+robot with a cancel button to refuse an action. For example in
+Figure~\ref{fig:gui} the robot proposes to move the eagle to the rat, and
+highlight (as shown by blue circles) the eagle and the rat. This indicate that
+features relevant to the eagle and the rat have been used to select this action.
+\begin{figure}
+        \centering
+    \includegraphics[width=80mm]{./fig/proposition.png}
+    \caption{Interface for the supervisor with an action being proposed, moving
+        eagle to rat with highlight of eagle and rat.}
+        \label{fig:gui}
+\end{figure}
+
+In the current implementation, the state is defined by the distance between each
+animals and their life. With these features selected, the partial state
+transmitted to the user is the distance between the eagle, the eagle's life and
+the rat's life. Similarly, when selected an action, the supervisor can also
+select features in the state relevant to the selction.
+
+Limitations of the approach reside in the difference of
+representation of the state and action spaces between the supervisor and the
+algorithm and limits in the communication. For example a user could try to move
+an animal close to another one,
+and depending of the represenation of the actions on the algorithm side, the
+action might not be understood in the same way. Similarly, features used by the
+supervisor to select actions might not be represented in the state used by the
+algorithm. And lastly, in the case of implicit selection of features, a single
+case of features representatin (for example highlighting two animals) might not
+be perceived in the same way by observers.
+
 %===============================================================================

### 2017-07-21 paper.tex
Update future work

@@
 
-This method still has to be tested in a real Human-Robot Interaction, and this
-evaluation is currently being implemented and will be tested in a near future.
+The system presented in the previous section will be improved and
+evaluated in the real world with children in the next months.
 
-The current work could be extended to allow the agent continue to improve its
-behaviour even in the absence of supervisor, progressively exploring around a learnt policy
-improving its policy beyond what have been taught. This
+The current work could also be extended to allow the agent continue to improve its
+behaviour even in the absence of supervisor, progressively exploring around the
+learnt policy improving its behaviour beyond the demonstrations. This
 could be done by allowing the supervisor to provide rewards during the learning
@@
 \cite{abbeel2004apprenticeship}. These could also use partial states associated
-to these rewards to have a general reward function despite a low number of
-datapoints.
+to these rewards to ease the generalisation of the reward function with only a
+low number of datapoints.
 But without the supervisor, the assumption that only a

### 2017-07-21 paper.tex
Pass on the abstract

@@
 %be accepted in human society robots have to learn how to interact with humans.
-Learning social interaction is a complex task. Firstly, no simulator of
-human interactions sufficiently precise exists today, so the learning will probably have
-to be made online and in the real world.
-This means that robots will have to learn directly from interacting with humans,
-which limits the quantity of datapoint possible to gather and make exploration
-riskier as actions will have real impacts on humans or the robot itself. Additionally,
-no clear reward function exists for social interactions. As such we argue that
+    Learning social interactions is a complex task that robots will have to
+    master before being accepted in society. However, as no simulator of human
+    interactions sufficiently
+    precise exists today, the learning have to be made online and in the real
+    world. Actions executed by the robot have impact on humans, and as such
+    have to be carefully selected, making the reliance on random exploration not
+    applicable. Additionally, no clear reward function exists for
+    social interactions. This implies that classical approaches such as
+    Reinforcement Learning cannot be directly applied. As such we argue that
     robots will highly profit from human expertise and guidance to learn social
-interactions. And as the quantity of data is limited, they also will have to make the most out of each datapoint. We
-propose to combine the Supervised Progressively Autonomous Robot Competencies
-allowing a safer online learning and Reinforcement Learning based on partial
-states rather than full states to accelerate the learning by using more
-information form the human teacher.
+    interactions. And as the quantity of input a human can provide is limited,
+    new methods have to be designed to use more efficiently human inputs. We
+    combine the Supervised Progressively Autonomous Robot Competencies (SPARC)
+    allowing a safer online learning with Reinforcement Learning based on
+    partial states rather than full states to accelerate the learning by
+    collecting and using more information from the human teacher.
 \end{abstract}

### 2017-07-21 paper.tex
Pass on the intro

@@
 to be able to learn new tasks, new actions policies, new social norms and how
-to make sense of the world surrounding them.
+to make sense of the world surrounding them as they are interacting in the world.
 
@@
  parts of the state can be irrelevant to the current goal and are not required
- to be taken into account to select the current action. A successful action
- policy maps these features to the relevant actions.
+ to be taken into account to select the current action, only a limited number of
+ features in the space are important. To interact efficiently, a robot has to
+ learn to identify these features and associate them to related actions.
 
-These relevant features in the space can be encoded in the representation of
-the space the robot uses for action selection or be learnt. Recent successes in Deep
-Learning~\cite{lecun2015deep} have shown that complex features can be extracted
-by neural networks assuming that enough datapoints are available.
+%These relevant features in the state space can be encoded in the representation of
+%the space the robot uses for action selection or be learnt. Recent successes in Deep
+%Learning~\cite{lecun2015deep} have shown that complex features can be extracted
+%by neural networks assuming that enough datapoints are available.
 
@@
 phase, the robot can compare these features, defined as partial states, with the
-current state to select an action based on which previously identify
-features are currently in the environment.
+current state to select an action based on which previously identified
+features are currently in the environment and submit it to its supervisor.
 

### 2017-07-21 paper.tex
Pass on background

@@
 In previous work~\cite{senft2015sparc,senft2017supervised}, we introduced the
-Supervised Progressively Autonomous Robot Competencies (SPARC), as a way to
+Supervised Progressively Autonomous Robot Competencies (SPARC), a way to
 teach a robot an action policy while interacting based on a supervisor
@@
 tries to maximise the reward. In many cases where RL achieves success, the agent
-had access to a virtual environment where the only real cost of exploring was 
+has access to a virtual environment where the only real cost of exploring is 
 time and energy, and the agent can interact as long as needed to gather
@@
 the victory of a computer in Backgammon back in the
-90s~\cite{tesauro1995temporal} or more recently the success achieved in playing
-Atari games based only on the image and the game rewards~\cite{mnih2015human}.
+90s~\cite{tesauro1995temporal} or more recently the success mastering the game
+of go~\cite{silver2016mastering}.
 
@@
 Initial knowledge has to be use in the designing of the algorithm, the
-representation of the state and actions spaces and the rewrd funtion. For
+representation of the state and actions spaces and the reward funtion. For
 example, only carefully crafted features allowed
@@
 informations in the reward function have important impacts on the ability of
-the robot to reach a successful policy.
+the robot to reach a successful policy~\cite{kober2013reinforcement}.
 
@@
 this approach, Abbeel and Ng achieved better than human control for a robotic
-helicopter~\cite{abbeel2004apprenticeship}.
+helicopter~\cite{abbeel2004apprenticeship} based on demonstrations from experts.
 
 \subsubsection{Guiding the learning:}
-
-In some cases, the state space is simply too big to rely only on random exploration to
-reach a successful action policy.Rather than solely providing initial knowledge
+Rather than solely providing initial knowledge
 to the agents, humans can also guide the agent throughout the learning in a more
@@
 This approach, known as "scaffolding" \cite{saunders2006teaching}, progressively
-increase the difficulty and complexity of the task or the environment as the
-robot is learning policies to achieve complex task not directly learnable in the final
-environment.
+increase the difficulty and complexity of the task as the robot is learning
+reaching policies not directly learnable in the final environment.
 
@@
 rewards to the current policy and performance of the agent, for example starting to reward
-positively suboptimal behaviours but which still improve the current policy and
-later, as the agent improve its behaviour reward these same suboptimal behaviour
-negatively and only the optimal ones positively.
+positively suboptimal behaviours but better than the current policy and
+later, as the agent improve its behaviour, reward these same suboptimal
+behaviours negatively and only the optimal ones positively.
 
@@
 supply  an agent both rewards and potential guidance or advise indicating where
-the agent should pay attention, or what it should do next. And they show that
+the agent should pay attention, or what it should do next. They show that
 giving the power to the supervisor to bias the action selection can improve the
-learning, making it faster, safer.
+learning, making it faster and safer.
 
 In \cite{senft2015sparc}, we introduced the Supervised Progressively
-Autonomous Robot Competencies (SPARC). SPARC relies on the presence of a
-supervisor teaching a robot how to interact in an environment. This teacher
-knowns which actions the robot is about to execute and can cancel an action or
-select another to be executed. Based on the supervisor's decisions, the robot
-learns which actions are desired and can refine its policy over time reducing
-the need for the teacher to correct or select an action.
+Autonomous Robot Competencies (SPARC). SPARC relies on supervisor with the
+ability to control the robot's actions. This teacher is presented with the
+actions the robot is about to execute and can cancel an action, let it be
+executed or select another to be executed. Based on the supervisor's decisions,
+the robot learns which actions are desired and can refine its policy over time
+reducing the need for the teacher to correct or select an action.
 
@@
 was not making use of any kind of generalisation, directly mapping a
-single (state,action) pair to a reward, and as such is not applicable to
+single (state, action) pair to a reward, and as such is not applicable to
 environments with a continuous or high dimensional space or undeterministic

### 2017-07-21 paper.tex
Pass on Partial States

@@
 
-\section{Partial-State Supervised Reinforcement Learning}
+\section{Partial State Supervised Reinforcement Learning}
 \begin{comment}
@@
 associate them to actions. This shifts the state action pair paradigm to a
-partial-state action pair, and in the case of RL, the tuple: partial-state,
+partial state action pair, and in the case of RL, the tuple: partial state,
 action and reward. 
@@
 A classical approach is to use a first layer of neural
-network or to use deep reinforcement learning which relies on deep neural
+network or to use deep reinforcement learning relying on deep neural
 networks to learn a mapping state action Qvalue for example. 
 These approaches, neural network based, relies on having a large number of
-datapoints to converge toward a good function approximator. However, as
-discussed previously, in many application, these amounts of data are not
-possible to be obtained and methods to generalise quickly are more desirable.
+datapoints to converge toward a good function approximator. However, 
+ in many application, especially HRI, these amounts of data are not
+obtainable due to time or unconsistency and methods to generalise with a lower
+number of inputs are required.
 
@@
 the environment to reduce the state dimension of the points stored in memory.
-We introduce the concept of partial-state, a sliced version of the state defined
+We introduce the concept of partial state, a sliced version of the state defined
 only on a subset of the dimensions of the state. This shifts the (state,action)
-pair paradigm to (partial-state,action)  
-and in the case of RL, the tuple (state, action, reward) to (partial-state,
-action, reward).
+pair paradigm to (partial state,action)  
+and in the case of RL, the tuple (state, action, reward) to (partial state,
+action, reward) and as such allows to compare the current state and the
+datapoints only on relevant features for action selection.
 
@@
 of the environment that can be sent to the algorithm to reduce the state associated
-to this action to a partial-state. Similarly, the algorithm can indicate which
+to this action to a partial state. Similarly, the algorithm can indicate which
 parts of the states have been used for the selection to the supervisor who can
@@
 An expert supervises the agent actions, and can assign rewards to actions and
-highlight the part of the states which are relevant to assigning this reward to
-this partial-state.
+highlight the parts of the states which are relevant to assigning this reward to
+this partial state.
 
@@
 to a set of actions $\mathcal{A}$, a state $\mathcal{S} \in [0,1]^{n}$. We
-also define the partial-states $\mathcal{s'} \in [0,1]^{n'}$ with $n' \leq n$ as a
+also define the partial states $\mathcal{S'} \in [0,1]^{n'}$ with $n' \leq n$ as a
 slice of $\mathcal{S}$, a subset of $\mathcal{S}$ where some dimensions have
@@
 At the instant $t$, the agent has access the state $s$, an action $a$, evaluated
-with a reward $r$ associated to the partial-state $s'$. For example, a state $s$ could be
+with a reward $r$ associated to the partial state $s'$. For example, a state $s$ could be
 defined in 4 dimensions such as ${s=[1,0.2,0,0.5]}$, and $s'$ in two dimensions with
 ${s'=[-,0.2,0,-]}$ with symbol '$-$' reprensenting the dimensions removed. The
-action $a$ has been evaluated $r$ in the partial-state $s'$.
+action $a$ has been evaluated $r$ in the partial state $s'$.
 
@@
 representing the rating done by the supervisor to action $a$ with feature
-highlighted for $s'$. When adding a new pairt $(s',r)$, we can discard all the
+highlighted for $s'$. When adding a new pairt $(s',r)$, we can discard potential
 previous pairs with an identical $s'$ to represent the evolution of the policy
@@
     \ForEach{$a \in \mathcal{A}$}{
-        \ForEach{$(s'-r) \in \mathcal{C}_{a}$}{
+        \ForEach{$p=(s',r) \in \mathcal{C}_{a}$}{
             compute similarity $\Delta$ between $s$ and $s'$:
-            $\Delta(s')=1-\frac{\sum_{i}^{n'}(s'(i)-s(i))^{2}}{n'}$
+            $\Delta(p)=1-\frac{\sum_{i}^{n'}(s'(i)-s(i))^{2}}{n'}$
         }
-        compute expected reward $\hat{r}(a)$:
-        $\hat{r}(a) = max(\Delta) \cdot r(arg\, max_{s'} \Delta(s'))$\\
-        with $r(\Delta(s'))$ reward of $(s'-r)$ pair
+        compute expected reward $\hat{r}(a)$ for taking $a$ in $s$:
+        $\hat{r}(a) = max(\Delta) \cdot r(arg\, max_{p} \Delta(p))$\\
+        with $r(\Delta(p))$ the reward of $p = (s',r)$ 
     }
+    Select the action with the maximum expected reward:
     $\pi(s) = arg\, max_{a} \hat{r}(a)$
@@
     \caption{Algorithm for selecting an action based on previous
-    partial-state action rewards tuples and current state}
+    partial state action rewards tuples and current state}
     \label{algo}
@@
 expected reward defined by the product between the similarity of the closest
-partial-state known for $a$ and the reward obtained in that partial-state.
+partial state known for $a$ and the reward obtained for executing $a$ in that partial state.
 Finally, the action with the highest expected reward can be selected.
@@
 When selecting an action with following Algorithm~\ref{algo}, the agent can also use
-the dimensions of the similar state $s'$ used for the selection to indicate the
+the dimensions of the close state $s'$ used for the selection to indicate the
 supervisor which parts of the state have been used for the action selection.
@@
 SPARC has been showed to be compatible with RL in \cite{senft2017supervised},
-and can also be easily combined with the approach presented in paper using
+and can also be easily combined with the approach presented in this paper using
 partial states. For example, when selecting an action for the robot to be
 executed, the supervisor can also select which features in the environment
-should be selected in the partial state, and this associate the reward +1
+should be selected in the partial state, and this associates the reward +1
 to this action in this partial state. Similarly when an action is
-proposed
-to the supervisor the dimensions features represented by the dimensions of the
-closest partial state can be explosed to the supervisor as a way to explain why
+proposed to the supervisor the features represented by the dimensions of the
+closest partial state can be exposed to the supervisor as a way to explain why
 this action has been selected. Facing this, the supervisor can not react,
 letting the action being executed and associating a reward of +1 to the partial
-state and the action proposed, the supervisor could also change the partial
-state to correct the features related to this action or cancel it, preventing the
-execution and associating a reward of -1.
+state and the action proposed, change the partial state to correct the features
+related to this action or cancel it, preventing the execution and associating a
+reward of -1.
 

### 2017-07-21 paper.tex
Pass on example and future work

@@
 animals and their life. With these features selected, the partial state
-transmitted to the user is the distance between the eagle, the eagle's life and
-the rat's life. Similarly, when selected an action, the supervisor can also
-select features in the state relevant to the selction.
+transmitted to the user is the distance between the eagle and the rat, the eagle's life and
+the rat's life. Similarly, when selecting an action, the supervisor can 
+select features in the state relevant to the selection.
 
-Limitations of the approach reside in the difference of
+The main limitations of the approach reside in the difference of
 representation of the state and action spaces between the supervisor and the
-algorithm and limits in the communication. For example a user could try to move
+algorithm and the limit in communication. For example a user could try to move
 an animal close to another one,
@@
 algorithm. And lastly, in the case of implicit selection of features, a single
-case of features representatin (for example highlighting two animals) might not
+case of features representatiion (for example highlighting two animals) might not
 be perceived in the same way by observers.

### 2017-07-24 paper.tex
Minor fixes

@@
     precise exists today, the learning have to be made online and in the real
-    world. Actions executed by the robot have impact on humans, and as such
+    world. Actions executed by the robot have impacts on humans, and as such
     have to be carefully selected, making the reliance on random exploration not
@@
     social interactions. This implies that classical approaches such as
-    Reinforcement Learning cannot be directly applied. As such we argue that
+    Reinforcement Learning cannot be directly applied for learning how to
+    interact with humans. As such we argue that
     robots will highly profit from human expertise and guidance to learn social
@@
     combine the Supervised Progressively Autonomous Robot Competencies (SPARC)
-    allowing a safer online learning with Reinforcement Learning based on
-    partial states rather than full states to accelerate the learning by
-    collecting and using more information from the human teacher.
+    allowing a safer online learning with Reinforcement Learning and use
+    partial states rather than full states to accelerate generalisation and
+    obtain more quickly a usable action policy.
 \end{abstract}
@@
 select actions appropriated to the current space. However,
- parts of the state can be irrelevant to the current goal and are not required
+ parts of the state can be irrelevant to the current goal or current state and
+ are not required
  to be taken into account to select the current action, only a limited number of
@@
 the agent learns an action policy to maximise the expected cummulative discounted
-reward obtained by the agent.
+reward received.
 
-Classic approaches in RL generally rely on exploring virtual environments where the agent
-tries to maximise the reward. In many cases where RL achieves success, the agent
+%Classic approaches in RL generally rely on exploring virtual environments where the agent
+%tries to maximise the reward.
+In many cases where RL achieves success, the agent
 has access to a virtual environment where the only real cost of exploring is 
@@
 90s~\cite{tesauro1995temporal} or more recently the success mastering the game
-of go~\cite{silver2016mastering}.
+of go~\cite{silver2016mastering}. Even where a virtual environment is available,
+but especially when it is not, human knowledge is required at many steps of the
+design of the algorithm or the learning phase to achieve an efficient action
+policy.
 
@@
 complex neural networks for state generalisation, the representation of actions
-as motor primitive rather than raw motor angles or adding additional
-informations in the reward function have important impacts on the ability of
+as motor primitives rather than raw motor angles or adding additional
+information in the reward function have important impacts on the ability of
 the robot to reach a successful policy~\cite{kober2013reinforcement}.
@@
 Authors of \cite{silver2016mastering} started with
-supervised learning from go master's games to learn a decent policy and then
+supervised learning from go masters' games to learn a decent policy and then
 used deep learning, self play and tree search to achieve super-human
-capabilities and beating humans best players.
+capabilities and beating human best players.
 
@@
 derives it from a set of expert demonstrations. The agent can then explore
-around the demonstrated policy to find how to optimise the reward function. With
+around the demonstrated policy to optimise the reward function. With
 this approach, Abbeel and Ng achieved better than human control for a robotic
-helicopter~\cite{abbeel2004apprenticeship} based on demonstrations from experts.
+helicopter~\cite{abbeel2004apprenticeship} based on demonstrations from experts
+and further exploration and autonomous learning.
 
@@
 
-A first approach consists in sequencing tasks the robot will face. 
+A first approach consists in sequencing the tasks the robot will face. 
 This approach, known as "scaffolding" \cite{saunders2006teaching}, progressively
-increase the difficulty and complexity of the task as the robot is learning
+increases the difficulty and complexity of the task as the robot is learning
 reaching policies not directly learnable in the final environment.
 
-A second approach is "shaping". For example, the TAMER framework
-\cite{knox2009interactively}, allows to teach an agent an action policy in an
-environment providing no rewards using a human observer to supply rewards to the
-agent. With this approach the teacher can adapt the
+Approaches from animal conditioning have also been transfered to Machine Learning. 
+For example, the TAMER framework~\cite{knox2009interactively} is an adaptation of "shaping",
+tuning an animal's behaviour by providing rewards to guide it to the desired
+behaviour. Unlike other RL setups, with TAMER, the
+reward is not provided by the environment but by a human observer. With this
+approach the teacher can adapt the 
 rewards to the current policy and performance of the agent, for example starting to reward
@@
 In \cite{senft2015sparc}, we introduced the Supervised Progressively
-Autonomous Robot Competencies (SPARC). SPARC relies on supervisor with the
+Autonomous Robot Competencies (SPARC). SPARC relies on a supervisor with the
 ability to control the robot's actions. This teacher is presented with the
-actions the robot is about to execute and can cancel an action, let it be
+actions the robot is about to execute and can cancel an action about to be
+executed, let it be
 executed or select another to be executed. Based on the supervisor's decisions,
@@
 SPARC gives control on the robot actions to an expert, who can guide the
-exploration in the desired part of the environment and this ensures the robot's
+exploration in the desired part of the environment which ensures the robot's
 behaviour is consistently appropriate. As the exploration is
@@
 have been explicitely or implicitely approved by the supervisor. However this method
-was not making use of any kind of generalisation, directly mapping a
-single (state, action) pair to a reward, and as such is not applicable to
+was  directly mapping a single (state, action) pair to a reward without making
+use of any kind of generalisation, it was not applicable to
 environments with a continuous or high dimensional space or undeterministic
-transition from one state to another.
+transition from one state to another, such as interactions with humans.
 
@@
 datapoints to converge toward a good function approximator. However, 
- in many application, especially HRI, these amounts of data are not
-obtainable due to time or unconsistency and methods to generalise with a lower
-number of inputs are required.
+ in many application, especially in HRI, these amounts of data are not
+obtainable due to time or unconsistency of human reactions, so methods to
+generalise with a lower number of inputs are required.
 
@@
 In this paper we propose to use a human to highlight the relevant features of
-the environment to reduce the state dimension of the points stored in memory.
+the environment to reduce the state dimension of the points only to relevant
+information.
 We introduce the concept of partial state, a sliced version of the state defined
-only on a subset of the dimensions of the state. This shifts the (state,action)
-pair paradigm to (partial state,action)  
+only on a subset of the dimensions of the state. This shifts the (state, action)
+pair paradigm to (partial state, action)  
 and in the case of RL, the tuple (state, action, reward) to (partial state,
-action, reward) and as such allows to compare the current state and the
+action, reward). This allows to compare the current state and the
 datapoints only on relevant features for action selection.
@@
 As the supervisor can estimate the future impacts of an action, the problem of
-credit assignment for delayed rewards can be ignored  and allows us to consider
+credit assignment for delayed rewards can be ignored which allows us to consider
 only a myopic approach.
@@
 Process to identify the different elements of our system. The agent has access
-to a set of actions $\mathcal{A}$, a state $\mathcal{S} \in [0,1]^{n}$. We
+to a set of actions $\mathcal{A}$ and a state $\mathcal{S} \in [0,1]^{n}$. We
 also define the partial states $\mathcal{S'} \in [0,1]^{n'}$ with $n' \leq n$ as a
@@
 
-At the instant $t$, the agent has access the state $s$, an action $a$, evaluated
-with a reward $r$ associated to the partial state $s'$. For example, a state $s$ could be
+When the agent execute an action $a$ in state $s$, it receives the reward $r$
+associated with the partial state $s'$. For example, a state $s$ could be
 defined in 4 dimensions such as ${s=[1,0.2,0,0.5]}$, and $s'$ in two dimensions with
-${s'=[-,0.2,0,-]}$ with symbol '$-$' reprensenting the dimensions removed. The
-action $a$ has been evaluated $r$ in the partial state $s'$.
+${s'=[-,0.2,0,-]}$ with symbol '$-$' reprensenting the dimensions removed. For
+the learning algorithm, this means that the action $a$ has been evaluated $r$ in
+the partial state $s'$.
 
@@
 $a \in \mathcal{A}$ we can associate a set $\mathcal{C}_{a}$ of pairs $(s',r)$
-representing the rating done by the supervisor to action $a$ with feature
-highlighted for $s'$. When adding a new pairt $(s',r)$, we can discard potential
+representing the rating done by the supervisor to action $a$ with features
+highlighted for the multiple $s'$. When adding a new pairt $(s',r)$, we can discard potential
 previous pairs with an identical $s'$ to represent the evolution of the policy
@@
     \caption{Algorithm for selecting an action based on previous
-    partial state action rewards tuples and current state}
+    partial state action rewards tuples and current state.}
     \label{algo}
@@
 closest partial state can be exposed to the supervisor as a way to explain why
-this action has been selected. Facing this, the supervisor can not react,
+this action has been selected. Facing this, the supervisor can: not react,
 letting the action being executed and associating a reward of +1 to the partial
@@
 related to this action or cancel it, preventing the execution and associating a
-reward of -1.
+reward of -1 to the partial state identified by the robot or the supervisor.
 
@@
 
-An example of application yet to be tested is robot for teaching to children.
+An example of application yet to be tested is robot for teaching children.
 A robot can play an educative game with children to teach them notions about
@@
 an animal close to another one,
-and depending of the represenation of the actions on the algorithm side, the
+and depending of the representation of the actions on the algorithm side, the
 action might not be understood in the same way. Similarly, features used by the
@@
 algorithm. And lastly, in the case of implicit selection of features, a single
-case of features representatiion (for example highlighting two animals) might not
+case of features representation (for example highlighting two animals) might not
 be perceived in the same way by observers.
@@
 The current work could also be extended to allow the agent continue to improve its
-behaviour even in the absence of supervisor, progressively exploring around the
+behaviour even in the absence of a supervisor, progressively exploring around the
 learnt policy improving its behaviour beyond the demonstrations. This
 could be done by allowing the supervisor to provide rewards during the learning
-phase, and combine these rewards with the demonstrations to learn a reward
+phase and combine these rewards with the demonstrations to learn a reward
 function in a fashion similar to Inverse Reinforcement Learning
-\cite{abbeel2004apprenticeship}. These could also use partial states associated
-to these rewards to ease the generalisation of the reward function with only a
-low number of datapoints.
+\cite{abbeel2004apprenticeship} or TAMER \cite{knox2009interactively}. This
+could also use partial states associated to these rewards to ease the
+generalisation of the reward function with only a low number of datapoints.
 But without the supervisor, the assumption that only a
@@
 %\section{Conclusion}
-\label{sec:conclusion}
+%\label{sec:conclusion}
 %==============================================================================

### 2017-07-26 paper.tex
Update on Overleaf.

@@
  \And Tony Belpaeme\\
- CRNS\\ Plymouth University (UK) \\ iMinds \\ Ghent University (Be)}
+ CRNS\\ Plymouth University (UK) \\ ID Lab -- imec \\ Ghent University (BE)}
 
@@
 %be accepted in human society robots have to learn how to interact with humans.
-    Learning social interactions is a complex task that robots will have to
-    master before being accepted in society. However, as no simulator of human
-    interactions sufficiently
-    precise exists today, the learning have to be made online and in the real
-    world. Actions executed by the robot have impacts on humans, and as such
-    have to be carefully selected, making the reliance on random exploration not
-    applicable. Additionally, no clear reward function exists for
+    Social interacting is a complex task for which machine learrning holds particular promise. However, as no sufficiently
+    accurate simulator of human interactions exists today, the learning of social interaction strategies has to happen online in the real
+    world. Actions executed by the robot impact on humans, and as such
+    have to be carefully selected, making it impossible to rely on random exploration. Additionally, no clear reward function exists for
     social interactions. This implies that classical approaches such as
     Reinforcement Learning cannot be directly applied for learning how to
-    interact with humans. As such we argue that
-    robots will highly profit from human expertise and guidance to learn social
+    interact with the social world. As such we argue that
+    robots will profit from human expertise and guidance to learn social
     interactions. And as the quantity of input a human can provide is limited,
-    new methods have to be designed to use more efficiently human inputs. We
-    combine the Supervised Progressively Autonomous Robot Competencies (SPARC)
-    allowing a safer online learning with Reinforcement Learning and use
+    new methods have to be designed to use human input more efficiently. In this paper we describe a setpu in which We
+    combine a framework called Supervised Progressively Autonomous Robot Competencies (SPARC), which
+    allows safer online learning with Reinforcement Learning, with the use
     partial states rather than full states to accelerate generalisation and
@@
 
-Human-Robot Interaction (HRI) aims at having humans and robot living together
-in the society, interacting socially in many different environments and
+Human-Robot Interaction (HRI) studies how people and robot can co-exist in society, and how they can interact socially in different environments and
 contexts. Robot are expected to behave appropriately regardless of the domain
-of interaction. However, not all behaviours can be known in advance and be
-implemented in the robot before its deployment in the real world. Similarly to
- humans, robots need
-to be able to learn new tasks, new actions policies, new social norms and how
-to make sense of the world surrounding them as they are interacting in the world.
+of interaction.
+However, it is impossible to foresee all possible interaction outcomes in dynamic and open social domains, as such the robot's responses cannot be implemented in the robot before its deployment in the real world.
+Similar to
+how people learn, robots need to be able to learn how to complete tasks through learning and optimising action policies. This including learning social norms and how to make sense of the social world.
 
-For a robot, interacting in the real world requires to combine inputs
- from many sensors to create a space composed of large number dimensions and
-select actions appropriated to the current space. However,
- parts of the state can be irrelevant to the current goal or current state and
- are not required
- to be taken into account to select the current action, only a limited number of
+For a robot, interacting in the real world often requires taking in a diverse and large range of sensory inputs, which results in a high-dimensional sensory space.
+The robots then is required to select actions based on its current state in sensor space.
+However,
+ parts of the state can be irrelevant to the current goal, and
+ as such should not be taken into account when selecting the current action. Often, only a limited number of
  features in the space are important. To interact efficiently, a robot has to
- learn to identify these features and associate them to related actions.
+ learn to identify these salient features and associate them with appropriate actions.
 
@@
 Supervised Progressively Autonomous Robot Competencies (SPARC), a way to
-teach a robot an action policy while interacting based on a supervisor
-correcting actions about to be executed by the robot. In this paper, we propose
+teach a robot an action policy while interacting based on a human supervisor
+intervening and correcting actions before they were executed by the robot. In this paper, we propose
 to extend this approach to allow the supervisor to highlight features in the
-environment associated to the selected action. During the action selection
+environment relevant for the selected action. During the action selection
 phase, the robot can compare these features, defined as partial states, with the
-current state to select an action based on which previously identified
-features are currently in the environment and submit it to its supervisor.
+current state to select an action. The selected is presented to the human supervisor, who can either correct the action or approve it for execution.
 
@@
 Learning (RL)~\cite{kober2013reinforcement,sutton1998reinforcement}. In RL, an
-agent is interacting in an environment
-providing numerical reward in reaction to the agent's actions and
-the agent learns an action policy to maximise the expected cummulative discounted
-reward received.
+agent interacting in an environment
+receives numerical rewards in reaction to its actions. The agent subsequently learns an action policy to maximise the expected cummulative discounted reward.
 
@@
 has access to a virtual environment where the only real cost of exploring is 
-time and energy, and the agent can interact as long as needed to gather
-enough information on the environment to find a correct action policy. When
-these conditions are reunited, RL can achieve impressive results, as shown by
-the victory of a computer in Backgammon back in the
-90s~\cite{tesauro1995temporal} or more recently the success mastering the game
-of go~\cite{silver2016mastering}. Even where a virtual environment is available,
-but especially when it is not, human knowledge is required at many steps of the
-design of the algorithm or the learning phase to achieve an efficient action
-policy.
+computational effort: the agent can interact as long as needed to gather
+enough information on the environment and the result of its actions on the environment in order to find a sufficiently optimal action policy.
+Using simulation RL can achieve impressive results, as shown in RL learning to play Backgammon in the
+90s~\cite{tesauro1995temporal} to the more recent success in mastering the game
+of Go~\cite{silver2016mastering}. Even when a virtual environment is available,
+but especially when it is not, human knowledge and effort is required during the
+design of the algorithm or the learning phase before the learning can be successful.
 
@@
 \subsubsection{Design decisions:}
-Initial knowledge has to be use in the designing of the algorithm, the
+Initial knowledge has to be use in the design of the algorithm, the
 representation of the state and actions spaces and the reward funtion. For
@@
 \subsubsection{Demonstrations:}
-Initial knowledge can be provided to the agent learning through demonstrations.
-These demonstrations can be used to create an initial policy sufficiently
+Initial knowledge can be provided to the agent through demonstrations.
+These demonstrations can be used to create an initial policy which is sufficiently
 efficient to start interacting in the environment and gather information to
@@
 size contains more than $10^{210}$ states, so exhaustive search is not possible.
-Authors of \cite{silver2016mastering} started with
-supervised learning from go masters' games to learn a decent policy and then
-used deep learning, self play and tree search to achieve super-human
-capabilities and beating human best players.
+Silver et al. \cite{silver2016mastering} started with
+supervised learning from Go masters' games to learn a decent enough policy and then
+proceeded using deep learning, self play and tree search to achieve super-human
+capabilities and beating the best human players.
 
@@
 Reinforcement Learning, the agent is not provided with a reward function, but
-derives it from a set of expert demonstrations. The agent can then explore
+derives it instead from a set of expert demonstrations. The agent can then explore
 around the demonstrated policy to optimise the reward function. With
@@
 Rather than solely providing initial knowledge
-to the agents, humans can also guide the agent throughout the learning in a more
-human-like teaching manner.
+to the agents, humans can also guide the agent during its learning, a method more resembling human teaching.
 
 A first approach consists in sequencing the tasks the robot will face. 
-This approach, known as "scaffolding" \cite{saunders2006teaching}, progressively
+This approach, known as ``scaffolding'' \cite{saunders2006teaching}, progressively
 increases the difficulty and complexity of the task as the robot is learning
-reaching policies not directly learnable in the final environment.
+to reach policies which would take prohibitively long without scaffolding.
 
 Approaches from animal conditioning have also been transfered to Machine Learning. 
-For example, the TAMER framework~\cite{knox2009interactively} is an adaptation of "shaping",
+For example, the TAMER framework~\cite{knox2009interactively} is an adaptation of ``shaping'',
 tuning an animal's behaviour by providing rewards to guide it to the desired
@@
 approach the teacher can adapt the 
-rewards to the current policy and performance of the agent, for example starting to reward
-positively suboptimal behaviours but better than the current policy and
-later, as the agent improve its behaviour, reward these same suboptimal
+rewards to the current policy and performance of the agent, for example starting to positively reward
+ suboptimal behaviours that are better than the current policy and
+later, as the agent improves its behaviour, reward these same suboptimal
 behaviours negatively and only the optimal ones positively.
 
-Another approach to guide the the learning is to bias the action selection.
+Another approach to guide the learning is to bias the action selection.
 In~\cite{thomaz2008teachable}, the authors propose to use a human supervisor to
-supply  an agent both rewards and potential guidance or advise indicating where
-the agent should pay attention, or what it should do next. They show that
+supply an agent with both rewards and potential guidance indicating what
+the agent should pay attention to, or what action it should take next. They show that
 giving the power to the supervisor to bias the action selection can improve the
@@
 Autonomous Robot Competencies (SPARC). SPARC relies on a supervisor with the
-ability to control the robot's actions. This teacher is presented with the
-actions the robot is about to execute and can cancel an action about to be
-executed, let it be
-executed or select another to be executed. Based on the supervisor's decisions,
-the robot learns which actions are desired and can refine its policy over time
-reducing the need for the teacher to correct or select an action.
+ability to control the robot's actions. This supervisor is presented with the
+action the robot is about to execute. He can then choose to cancel it, allow it to be
+executed, or can select an alternative action. Based on the supervisor's decisions,
+the robot learns which actions are desired and can as such refine its policy over time
+reducing the need for the supervisor to correct or select an action.
 
-SPARC gives control on the robot actions to an expert, who can guide the
+SPARC gives control of the robot's actions to an expert, who can guide the
 exploration in the desired part of the environment which ensures the robot's
@@
     \includegraphics[width=0.9\linewidth]{./fig/motivation.pdf}
-    \caption{Idealised expectation for performance, autonomy and human workload for a
-    an autonomous learner, an approach using human rewards and SPARC.}
+    \caption{An illustration of the evoluation over time of the performance, autonomy and human workload for a
+    an autonomous learner, an approach using human rewards, and SPARC.}
     \label{fig:comparison}
@@
 In \cite{senft2017supervised}, we presented a way to combine SPARC and RL, by
-assigning a positive reward to every action executed by the robot as it would
-have been explicitely or implicitely approved by the supervisor. However this method
+assigning a positive reward to every action executed by the robot, making the assumption that every action has been explicitely or implicitely approved by the supervisor. However this method
 was  directly mapping a single (state, action) pair to a reward without making
-use of any kind of generalisation, it was not applicable to
-environments with a continuous or high dimensional space or undeterministic
-transition from one state to another, such as interactions with humans.
+use of any kind of generalisation. As such it was not applicable to
+environments with a continuous or high dimensional space or non-deterministic
+transitions from one state to another, elements which are typically present in social interactions.
 
@@
 requires a way to generalise knowledge to unseen states. 
-A classical approach is to use a first layer of neural
+A classic approach is to use a feed-forward neural
 network or to use deep reinforcement learning relying on deep neural
-networks to learn a mapping state action Qvalue for example. 
-These approaches, neural network based, relies on having a large number of
+networks to learn a the value function. 
+These approaches rely on having a large number of
 datapoints to converge toward a good function approximator. However, 
- in many application, especially in HRI, these amounts of data are not
-obtainable due to time or unconsistency of human reactions, so methods to
-generalise with a lower number of inputs are required.
+ in many applications and especially in HRI, these amounts of data are not
+available or obtainable due to practical constraints.
+Furthermore, human responses are often noisy and lack consistency, so methods are needed which can generalise from a low number of noise data points.
 
@@
 
-In this paper we propose to use a human to highlight the relevant features of
+In this paper we propose to use a human user to highlight the relevant features of
 the environment to reduce the state dimension of the points only to relevant
 information.
-We introduce the concept of partial state, a sliced version of the state defined
+We introduce the concept of a partial state, a sliced version of the state defined
 only on a subset of the dimensions of the state. This shifts the (state, action)
@@
 
-When the agent execute an action $a$ in state $s$, it receives the reward $r$
+When the agent executes an action $a$ in state $s$, it receives the reward $r$
 associated with the partial state $s'$. For example, a state $s$ could be
@@
 
-    \caption{Algorithm for selecting an action based on previous
-    partial state action rewards tuples and current state.}
+    \caption{Algorithm for selecting an action based on the previous
+    (partial state, action, reward) tuples and the current state.}
     \label{algo}
@@
 
-When selecting an action with following Algorithm~\ref{algo}, the agent can also use
+When selecting an action, the agent can also use
 the dimensions of the close state $s'$ used for the selection to indicate the
@@
 
-SPARC has been showed to be compatible with RL in \cite{senft2017supervised},
+SPARC has been shown to be compatible with RL in \cite{senft2017supervised},
 and can also be easily combined with the approach presented in this paper using
@@
 executed, the supervisor can also select which features in the environment
-should be selected in the partial state, and this associates the reward +1
-to this action in this partial state. Similarly when an action is
+should be selected as the partial state, and this associates the reward 
+to this action in this partial state. Similarly, when an action is
 proposed to the supervisor the features represented by the dimensions of the
 closest partial state can be exposed to the supervisor as a way to explain why
-this action has been selected. Facing this, the supervisor can: not react,
-letting the action being executed and associating a reward of +1 to the partial
-state and the action proposed, change the partial state to correct the features
-related to this action or cancel it, preventing the execution and associating a
+this action has been selected. Facing this, the supervisor can: (1) not react,
+allowing the action to be executed and associating a reward of +1 to the partial
+state and the action proposed, (2) change the partial state to correct the features
+related to this action or (3) cancel it, preventing the execution and associating a
 reward of -1 to the partial state identified by the robot or the supervisor.
 
-\section{Example of application}
+\section{Application scenario}
 
-An example of application yet to be tested is robot for teaching children.
-A robot can play an educative game with children to teach them notions about
+An example of an application is a social robot which interacts with children in an educational scenario.
+The robot plays an educational game with children to teach them notions about
 diverse topics according to the needs of the teacher. For this example, a child
-and a robot are playing a game about food web, teaching wich animals eat which
+and a robot are playing a game about the food web, teaching wich animals eat which
 ones on a Sandtray~\cite{baxter2012touchscreen} as shown in
@@
 In the current implementation, the state is defined by the distance between each
-animals and their life. With these features selected, the partial state
+animal and their life. With these features selected, the partial state
 transmitted to the user is the distance between the eagle and the rat, the eagle's life and
 the rat's life. Similarly, when selecting an action, the supervisor can 
-select features in the state relevant to the selection.
+select features in the state relevant to the action.
 
@@
 an animal close to another one,
-and depending of the representation of the actions on the algorithm side, the
+and depending on the representation of the actions on the algorithm side, the
 action might not be understood in the same way. Similarly, features used by the
@@
 
-The current work could also be extended to allow the agent continue to improve its
+The current work could also be extended to allow the agent to continue to improve its
 behaviour even in the absence of a supervisor, progressively exploring around the

### 2017-07-26 paper.tex
Fixing typos

@@
 %be accepted in human society robots have to learn how to interact with humans.
-    Social interacting is a complex task for which machine learrning holds particular promise. However, as no sufficiently
+    Social interacting is a complex task for which machine learning holds particular promise. However, as no sufficiently
     accurate simulator of human interactions exists today, the learning of social interaction strategies has to happen online in the real
@@
     interactions. And as the quantity of input a human can provide is limited,
-    new methods have to be designed to use human input more efficiently. In this paper we describe a setpu in which We
+    new methods have to be designed to use human input more efficiently. In this paper we describe a setup in which We
     combine a framework called Supervised Progressively Autonomous Robot Competencies (SPARC), which
@@
 For a robot, interacting in the real world often requires taking in a diverse and large range of sensory inputs, which results in a high-dimensional sensory space.
-The robots then is required to select actions based on its current state in sensor space.
+The robot then is required to select actions based on its current state in sensor space.
 However,
@@
 phase, the robot can compare these features, defined as partial states, with the
-current state to select an action. The selected is presented to the human supervisor, who can either correct the action or approve it for execution.
+current state to select an action. The selected action is presented to the human supervisor, who can either correct the action or approve it for execution.
 
@@
 \subsubsection{Design decisions:}
-Initial knowledge has to be use in the design of the algorithm, the
+Initial knowledge has to be used in the design of the algorithm, the
 representation of the state and actions spaces and the reward funtion. For
@@
 available or obtainable due to practical constraints.
-Furthermore, human responses are often noisy and lack consistency, so methods are needed which can generalise from a low number of noise data points.
+Furthermore, human responses are often noisy and lack consistency, so methods are needed which can generalise from a low number of noisy data points.
 
@@
 proposed to the supervisor the features represented by the dimensions of the
-closest partial state can be exposed to the supervisor as a way to explain why
+closest partial state for this action can be exposed to the supervisor as a way to explain why
 this action has been selected. Facing this, the supervisor can: (1) not react,
@@
     \caption{Interface for the supervisor with an action being proposed, moving
-        eagle to rat with highlight of eagle and rat.}
+        the eagle to the rat with highlight of the eagle and the rat.}
         \label{fig:gui}

### 2017-07-26 paper.tex
Reorder for image position

@@
 and a robot are playing a game about the food web, teaching wich animals eat which
-ones on a Sandtray~\cite{baxter2012touchscreen} as shown in
-Figure~\ref{fig:game}. In addition to the child and
+ones on a Sandtray~\cite{baxter2012touchscreen}. In addition to the child and
 the robot, an adult supervises the robot using a tablet with a Graphical User
-Interface (GUI) (Figure~\ref{fig:gui}) to teach the robot how to interact with the child.
+Interface (GUI) to teach the robot how to interact with the child as shown in
+Figure~\ref{fig:setup}.
 \begin{figure}
         \centering
-  \includegraphics[width=80mm]{./fig/game.png} 
-    \caption{Game displayed on the Sandtray the child is playing with the robot.}
-        \label{fig:game}
+  \includegraphics[width=60mm]{./figs/setup} 
+    \caption{Interaction setup: the child and the robot are interacting on the
+    touchscreen and a supervisor can control the robot using a GUI on a tablet.}
+        \label{fig:setup}
 \end{figure}
 
-As shown in Figures \ref{fig:game} and \ref{fig:gui}, the GUI is an augmented
+The GUI (shown in Figure \ref{fig:gui} is an augmented
 version of the game itself, which can be use to make the robot move items on the
@@
 features relevant to the eagle and the rat have been used to select this action.
+
+In the current implementation, the state is defined by the distance between each
+animal and their energy. With these features selected, the partial state
+transmitted to the user is the distance between the eagle and the rat, the
+eagle's energy and
+the rat's energy. Similarly, when selecting an action, the supervisor can 
+select features in the state relevant to the action.
+
 \begin{figure}
         \centering
-    \includegraphics[width=80mm]{./fig/proposition.png}
+    \includegraphics[width=60mm]{./figs/proposition.png}
     \caption{Interface for the supervisor with an action being proposed, moving
@@
 \end{figure}
-
-In the current implementation, the state is defined by the distance between each
-animal and their life. With these features selected, the partial state
-transmitted to the user is the distance between the eagle and the rat, the eagle's life and
-the rat's life. Similarly, when selecting an action, the supervisor can 
-select features in the state relevant to the action.
 

### 2017-07-26 paper.tex
{fig->figs} and add setup fig

@@
     \centering
-    \includegraphics[width=0.9\linewidth]{./fig/motivation.pdf}
-    \caption{An illustration of the evoluation over time of the performance, autonomy and human workload for a
+    \includegraphics[width=0.9\linewidth]{./figs/motivation.pdf}
+    \caption{An illustration of the evolution over time of the performance, autonomy and human workload for a
     an autonomous learner, an approach using human rewards, and SPARC.}

### 2017-07-26 paper.tex
removing weirdly formulated sentence
Reorganisation

@@
 
-To each action
-$a \in \mathcal{A}$ we can associate a set $\mathcal{C}_{a}$ of pairs $(s',r)$
-representing the rating done by the supervisor to action $a$ with features
-highlighted for the multiple $s'$. When adding a new pairt $(s',r)$, we can discard potential
-previous pairs with an identical $s'$ to represent the evolution of the policy
-evaluation by the supervisor.
-
 \begin{algorithm}
@@
 
+To each action
+$a \in \mathcal{A}$ we can associate a set $\mathcal{C}_{a}$ of pairs $(s',r)$
+representing the rating done by the supervisor to action $a$ with features
+highlighted for the multiple $s'$. When adding a new pairt $(s',r)$, we can discard potential
+previous pairs with an identical $s'$ to represent the evolution of the policy
+evaluation by the supervisor.
+
 When facing a new state $s$ where an action has to be
@@
 
-When selecting an action, the agent can also use
-the dimensions of the close state $s'$ used for the selection to indicate the
-supervisor which parts of the state have been used for the action selection.
+%When selecting an action, the agent can also use
+%the dimensions of the close state $s'$ used for the selection to indicate the
+%supervisor which parts of the state have been used for the action selection.
 
@@
 
+\begin{figure}
+        \centering
+  \includegraphics[width=60mm]{./figs/setup} 
+    \caption{Interaction setup: the child and the robot are interacting on the
+    touchscreen and a supervisor can control the robot using a GUI on a tablet.}
+        \label{fig:setup}
+\end{figure}
+
 An example of an application is a social robot which interacts with children in an educational scenario.
@@
 Figure~\ref{fig:setup}.
-\begin{figure}
-        \centering
-  \includegraphics[width=60mm]{./figs/setup} 
-    \caption{Interaction setup: the child and the robot are interacting on the
-    touchscreen and a supervisor can control the robot using a GUI on a tablet.}
-        \label{fig:setup}
-\end{figure}
 
-The GUI (shown in Figure \ref{fig:gui} is an augmented
+The GUI (Figure \ref{fig:gui}) is an augmented
 version of the game itself, which can be use to make the robot move items on the

### 2017-07-26 paper.tex
Reorganisation
Update on Overleaf.

@@
   \pdfinfo{
-/Title (Supervised Reinforcement Learning with Partial States: a Teaching Method for Action Selection for HRI)
+/Title (Toward Supervised Reinforcement Learning with Partial States for Social HRI)
 /Author (Emmanuel Senft)}
@@
 %
-\title{Supervised Reinforcement Learning with Partial States: \\
- a Teaching Method for Action Selection for HRI}
+\title{Toward Supervised Reinforcement Learning with Partial States for Social HRI}
 
@@
 
+To each action
+$a \in \mathcal{A}$ we can associate a set $\mathcal{C}_{a}$ of pairs $(s',r)$
+representing the rating done by the supervisor to action $a$ with features
+highlighted for the multiple $s'$. When adding a new pairt $(s',r)$, we can discard potential
+previous pairs with an identical $s'$ to represent the evolution of the policy
+evaluation by the supervisor.
+
 \begin{algorithm}
@@
 \end{algorithm}
-
-To each action
-$a \in \mathcal{A}$ we can associate a set $\mathcal{C}_{a}$ of pairs $(s',r)$
-representing the rating done by the supervisor to action $a$ with features
-highlighted for the multiple $s'$. When adding a new pairt $(s',r)$, we can discard potential
-previous pairs with an identical $s'$ to represent the evolution of the policy
-evaluation by the supervisor.
 
@@
 
-\begin{figure}
-        \centering
-  \includegraphics[width=60mm]{./figs/setup} 
-    \caption{Interaction setup: the child and the robot are interacting on the
-    touchscreen and a supervisor can control the robot using a GUI on a tablet.}
-        \label{fig:setup}
-\end{figure}
-
 An example of an application is a social robot which interacts with children in an educational scenario.
@@
 Figure~\ref{fig:setup}.
+
+\begin{figure}
+        \centering
+  \includegraphics[width=60mm]{./figs/setup} 
+    \caption{Interaction setup: the child and the robot are interacting on the
+    touchscreen and a supervisor can control the robot using a GUI on a tablet.}
+        \label{fig:setup}
+\end{figure}
 

### 2017-08-22 paper.tex
Fix typos and paragraph normalisation

@@
 
-\maketitle
-\begin{abstract}
+\maketitle \begin{abstract}
 %As robots will integrate human society, they will have to satify humans'
-%expectations. However at the design time, it seems hardly possible to
-%know in advance exactly all the behaviours expected from the robot. As such to
-%be accepted in human society robots have to learn how to interact with humans.
-    Social interacting is a complex task for which machine learning holds particular promise. However, as no sufficiently
-    accurate simulator of human interactions exists today, the learning of social interaction strategies has to happen online in the real
-    world. Actions executed by the robot impact on humans, and as such
-    have to be carefully selected, making it impossible to rely on random exploration. Additionally, no clear reward function exists for
-    social interactions. This implies that classical approaches such as
+    %expectations. However at the design time, it seems hardly possible to know
+    %in advance exactly all the behaviours expected from the robot. As such to
+    %be accepted in human society robots have to learn how to interact with
+    %humans.
+    Social interacting is a complex task for which machine learning holds
+    particular promise. However, as no sufficiently accurate simulator of human
+    interactions exists today, the learning of social interaction strategies has
+    to happen online in the real world. Actions executed by the robot impact on
+    humans, and as such have to be carefully selected, making it impossible to
+    rely on random exploration. Additionally, no clear reward function exists
+    for social interactions. This implies that traditional approaches used for
     Reinforcement Learning cannot be directly applied for learning how to
-    interact with the social world. As such we argue that
-    robots will profit from human expertise and guidance to learn social
-    interactions. And as the quantity of input a human can provide is limited,
-    new methods have to be designed to use human input more efficiently. In this paper we describe a setup in which We
-    combine a framework called Supervised Progressively Autonomous Robot Competencies (SPARC), which
-    allows safer online learning with Reinforcement Learning, with the use
-    partial states rather than full states to accelerate generalisation and
-    obtain more quickly a usable action policy.
+    interact with the social world. As such we argue that robots will profit
+    from human expertise and guidance to learn social interactions. And as the
+    quantity of input a human can provide is limited, new methods have to be
+    designed to use human input more efficiently. In this paper we describe a
+    setup in which we combine a framework called Supervised Progressively
+    Autonomous Robot Competencies (SPARC), which allows safer online learning
+    with Reinforcement Learning, with the use partial states rather than full
+    states to accelerate generalisation and obtain more quickly a usable action
+    policy.  
 \end{abstract}
@@
 
-Human-Robot Interaction (HRI) studies how people and robot can co-exist in society, and how they can interact socially in different environments and
+Human-Robot Interaction (HRI) studies how people and robot can co-exist in
+ society, and how they can interact socially in different environments and
  contexts. Robot are expected to behave appropriately regardless of the domain
-of interaction.
-However, it is impossible to foresee all possible interaction outcomes in dynamic and open social domains, as such the robot's responses cannot be implemented in the robot before its deployment in the real world.
-Similar to
-how people learn, robots need to be able to learn how to complete tasks through learning and optimising action policies. This including learning social norms and how to make sense of the social world.
+ of interaction. However, it is impossible to foresee all possible interaction
+ outcomes in dynamic and open social domains, as such the robot's responses
+ cannot be implemented in the robot before its deployment in the real world.
+ Similarly to  people, robots need to be able to learn how to complete tasks
+ throug creating and optimising action policies. This includes learning social
+ norms and how to make sense of the social world.
 
-For a robot, interacting in the real world often requires taking in a diverse and large range of sensory inputs, which results in a high-dimensional sensory space.
-The robot then is required to select actions based on its current state in sensor space.
-However,
- parts of the state can be irrelevant to the current goal, and
- as such should not be taken into account when selecting the current action. Often, only a limited number of
- features in the space are important. To interact efficiently, a robot has to
- learn to identify these salient features and associate them with appropriate actions.
+For a robot, interacting in the real world often requires taking in a diverse
+ and large range of sensory inputs, which results in a high-dimensional sensory
+ space. The robot then is required to select actions based on its current state
+ in sensor space. However, parts of the state can be irrelevant to the current
+ goal, and as such should not be taken into account when selecting the current
+ action. Often, only a limited number of features in the space are important. To
+ interact efficiently, a robot has to learn to identify these salient features
+ and associate them with appropriate actions.
 
@@
 In previous work~\cite{senft2015sparc,senft2017supervised}, we introduced the
-Supervised Progressively Autonomous Robot Competencies (SPARC), a way to
-teach a robot an action policy while interacting based on a human supervisor
-intervening and correcting actions before they were executed by the robot. In this paper, we propose
-to extend this approach to allow the supervisor to highlight features in the
-environment relevant for the selected action. During the action selection
+Supervised Progressively Autonomous Robot Competencies (SPARC), a way to teach a
+robot an action policy while interacting based on a human supervisor intervening
+and correcting actions before they were executed by the robot. In this paper, we
+propose to extend this approach to allow the supervisor to highlight features in
+the environment relevant for the selected action. During the action selection
 phase, the robot can compare these features, defined as partial states, with the
-current state to select an action. The selected action is presented to the human supervisor, who can either correct the action or approve it for execution.
+current state to select an action. The selected action is presented to the human
+supervisor, who can either correct the action or approve it for execution.
 
-\begin{comment}
-This approach in especially relevant for HRI as gathering datapoints has to be
-performed in the real world and interacting with humans forces a robot to have
-an appropriate action policy at anytime of the interaction. even in the early
-phase when the robot has no information about the way its environment react to
-its actions.
-
-When interacting in the real world, humans face huge spaces of almost unlimited
-dimensions, and despite this complexity, humans, and especially children are able
-to learn quickly, often from only a few demonstrations or examples. One of the
- reason could be that they are able to take the most out of every datapoint available to them. 
- On the other
-hand, recent impressive advances in Machine Learning such as Deep Learning~\cite{lecun2015deep}
-have been made possible by the availability of huge dataset covering millions
-of labeled examples or dozens of hours of recording. These progress have
-targetting either perception, where labeled datapoints can be available or
-action selection in virtual environments where the impact of actions is
-limited.
-
-However, these large labelled dataset or virtul worlds do not exist for
-social interaction. To learn how to interact with humans, robots have to
-experiment in the real world facing the actual reactions from their actions. As
-such they
-have to learn quickly while consistently exhibiting a acceptable behaviours.
-One way of ensuring this correct  behaviours is to rely on a human to supervise
-the robot during the early phase of learning, and this human can also provide
-inputs to boostrap the learning, achieving a faster learning. This paper present
-a novel method based on human supervision, feature highlighting and partial
-state reinforcement learning to achieve this fast and safe learning.
-\end{comment}
-%===============================================================================
+===============================================================================
 
@@
 The main framework for an agent to learn how to interact in an environment while
-interacting is Reinforcement 
-Learning (RL)~\cite{kober2013reinforcement,sutton1998reinforcement}. In RL, an
-agent interacting in an environment
-receives numerical rewards in reaction to its actions. The agent subsequently learns an action policy to maximise the expected cummulative discounted reward.
+interacting is Reinforcement Learning
+(RL)~\cite{kober2013reinforcement,sutton1998reinforcement}. In RL, an agent
+interacting in an environment receives numerical rewards in reaction to its
+actions. The agent subsequently learns an action policy to maximise the expected
+cummulative discounted reward.
 
-%Classic approaches in RL generally rely on exploring virtual environments where the agent
-%tries to maximise the reward.
-In many cases where RL achieves success, the agent
-has access to a virtual environment where the only real cost of exploring is 
-computational effort: the agent can interact as long as needed to gather
-enough information on the environment and the result of its actions on the environment in order to find a sufficiently optimal action policy.
-Using simulation RL can achieve impressive results, as shown in RL learning to play Backgammon in the
+%Classic approaches in RL generally rely on exploring virtual environments where
+%the agent tries to maximise the reward.
+In many cases where RL achieves success, the agent has access to a virtual
+environment where the only real cost of exploring is computational effort: the
+agent can interact as long as needed to gather enough information on the
+environment and the result of its actions on the environment in order to find a
+sufficiently optimal action policy. Using simulation RL can achieve impressive
+results, as shown in RL learning to play Backgammon in the
 90s~\cite{tesauro1995temporal} to the more recent success in mastering the game
@@
 but especially when it is not, human knowledge and effort is required during the
-design of the algorithm or the learning phase before the learning can be successful.
+design of the algorithm or the learning phase before the learning can be
+successful.
 
@@
 \subsubsection{Demonstrations:} 
-Initial knowledge can be provided to the agent through demonstrations.
-These demonstrations can be used to create an initial policy which is sufficiently
-efficient to start interacting in the environment and gather information to
-improve over time. This initial policy, required to receive meaningful feedback
-from the environment can be impossible to reach by relying only on random
-exploration and feedback from the environment. For example the game of Go in its larger board
-size contains more than $10^{210}$ states, so exhaustive search is not possible.
-Silver et al. \cite{silver2016mastering} started with
-supervised learning from Go masters' games to learn a decent enough policy and then
-proceeded using deep learning, self play and tree search to achieve super-human
-capabilities and beating the best human players.
+Initial knowledge can be provided to the agent
+through demonstrations. These demonstrations can be used to create an initial
+policy which is sufficiently efficient to start interacting in the environment
+and gather information to improve over time. This initial policy, required to
+receive meaningful feedback from the environment can be impossible to reach by
+relying only on random exploration and feedback from the environment. For
+example the game of Go in its larger board size contains more than $10^{210}$
+states, so exhaustive search is not possible.  Silver et al.
+\cite{silver2016mastering} started with supervised learning from Go masters'
+games to learn a decent enough policy and then proceeded using deep learning,
+self play and tree search to achieve super-human capabilities and beating the
+best human players.
 
@@
 Reinforcement Learning, the agent is not provided with a reward function, but
-derives it instead from a set of expert demonstrations. The agent can then explore
-around the demonstrated policy to optimise the reward function. With
+derives it instead from a set of expert demonstrations. The agent can then
+explore around the demonstrated policy to optimise the reward function. With
 this approach, Abbeel and Ng achieved better than human control for a robotic
@@
 \subsubsection{Guiding the learning:}
-Rather than solely providing initial knowledge
-to the agents, humans can also guide the agent during its learning, a method more resembling human teaching.
+Rather than solely providing initial knowledge to the agents, humans can also
+guide the agent during its learning, a method more resembling human teaching.
 
-A first approach consists in sequencing the tasks the robot will face. 
-This approach, known as ``scaffolding'' \cite{saunders2006teaching}, progressively
-increases the difficulty and complexity of the task as the robot is learning
-to reach policies which would take prohibitively long without scaffolding.
+A first approach consists in sequencing the tasks the robot will face.  This
+approach, known as ``scaffolding'' \cite{saunders2006teaching}, progressively
+increases the difficulty and complexity of the task as the robot is learning to
+reach policies which would take prohibitively long without scaffolding.
 
-Approaches from animal conditioning have also been transfered to Machine Learning. 
-For example, the TAMER framework~\cite{knox2009interactively} is an adaptation of ``shaping'',
-tuning an animal's behaviour by providing rewards to guide it to the desired
-behaviour. Unlike other RL setups, with TAMER, the
+Approaches from animal conditioning have also been transfered to Machine
+Learning.  For example, the TAMER framework~\cite{knox2009interactively} is an
+adaptation of ``shaping'', tuning an animal's behaviour by providing rewards to
+guide it to the desired behaviour. Unlike other RL setups, with TAMER, the
 reward is not provided by the environment but by a human observer. With this
-approach the teacher can adapt the 
-rewards to the current policy and performance of the agent, for example starting to positively reward
- suboptimal behaviours that are better than the current policy and
-later, as the agent improves its behaviour, reward these same suboptimal
-behaviours negatively and only the optimal ones positively.
+approach the teacher can adapt the rewards to the current policy and performance
+of the agent, for example starting to positively reward suboptimal behaviours
+that are better than the current policy and later, as the agent improves its
+behaviour, reward these same suboptimal behaviours negatively and only the
+optimal ones positively.
 
@@
 In~\cite{thomaz2008teachable}, the authors propose to use a human supervisor to
-supply an agent with both rewards and potential guidance indicating what
-the agent should pay attention to, or what action it should take next. They show that
-giving the power to the supervisor to bias the action selection can improve the
-learning, making it faster and safer.
+supply an agent with both rewards and potential guidance indicating what the
+agent should pay attention to, or what action it should take next. They show
+that giving the power to the supervisor to bias the action selection can improve
+the learning, making it faster and safer.
 
-In \cite{senft2015sparc}, we introduced the Supervised Progressively
-Autonomous Robot Competencies (SPARC). SPARC relies on a supervisor with the
-ability to control the robot's actions. This supervisor is presented with the
-action the robot is about to execute. He can then choose to cancel it, allow it to be
-executed, or can select an alternative action. Based on the supervisor's decisions,
-the robot learns which actions are desired and can as such refine its policy over time
-reducing the need for the supervisor to correct or select an action.
+In \cite{senft2015sparc}, we introduced the Supervised Progressively Autonomous
+Robot Competencies (SPARC). SPARC relies on a supervisor with the ability to
+control the robot's actions. This supervisor is presented with the action the
+robot is about to execute. He can then choose to cancel it, allow it to be
+executed, or can select an alternative action. Based on the supervisor's
+decisions, the robot learns which actions are desired and can as such refine its
+policy over time reducing the need for the supervisor to correct or select an
+action.
 
@@
 exploration in the desired part of the environment which ensures the robot's
-behaviour is consistently appropriate. As the exploration is
-guided, and all the actions are useful, the learning can be faster than
-autonomous learning or feedback based learning as illustrated in Figure
-\ref{fig:comparison}.
+behaviour is consistently appropriate. As the exploration is guided, and all the
+actions are useful, the learning can be faster than autonomous learning or
+feedback based learning as illustrated in Figure~\ref{fig:comparison}.
 
@@
     \includegraphics[width=0.9\linewidth]{./figs/motivation.pdf}
-    \caption{An illustration of the evolution over time of the performance, autonomy and human workload for a
-    an autonomous learner, an approach using human rewards, and SPARC.}
+    \caption{An illustration of the evolution over time of the performance,
+    autonomy and human workload for an autonomous learner, an approach using
+    human rewards, and SPARC.}
     \label{fig:comparison}
@@
 In \cite{senft2017supervised}, we presented a way to combine SPARC and RL, by
-assigning a positive reward to every action executed by the robot, making the assumption that every action has been explicitely or implicitely approved by the supervisor. However this method
-was  directly mapping a single (state, action) pair to a reward without making
-use of any kind of generalisation. As such it was not applicable to
-environments with a continuous or high dimensional space or non-deterministic
-transitions from one state to another, elements which are typically present in social interactions.
+assigning a positive reward to every action executed by the robot, making the
+assumption that every action has been explicitly or implicitely approved by the
+supervisor. However this method was  directly mapping a single (state, action)
+pair to a reward without making use of any kind of generalisation. As such it
+was not applicable to environments with a continuous or high dimensional space
+or non-deterministic transitions from one state to another, elements which are
+typically present in social interactions.
 
 \section{Partial State Supervised Reinforcement Learning}
-\begin{comment}
-Humans evolve in a highly complex environment with a nearly infinite number of
-dimensions originating from different modality through our senses. But, despite
-this complexity, we can select actions according to important features of the
-state, regardless of other parts of it.
-
-Taking inspiration from this observation, we argue that focusing on partial states, rather
-than full states can both increase the speed of learning for an agent and
-provide some of the generalisation required to interact in complex environment.
-Guidance from a human can highlight important features in the state space and
-associate them to actions. This shifts the state action pair paradigm to a
-partial state action pair, and in the case of RL, the tuple: partial state,
-action and reward. 
-\end{comment}
 
 To make RL applicable in high dimensional or continuous states, the algorithm
-requires a way to generalise knowledge to unseen states. 
-A classic approach is to use a feed-forward neural
-network or to use deep reinforcement learning relying on deep neural
-networks to learn a the value function. 
-These approaches rely on having a large number of
-datapoints to converge toward a good function approximator. However, 
- in many applications and especially in HRI, these amounts of data are not
-available or obtainable due to practical constraints.
-Furthermore, human responses are often noisy and lack consistency, so methods are needed which can generalise from a low number of noisy data points.
+requires a way to generalise knowledge to unseen states.  A classic approach is
+to use a feed-forward neural network or to use deep reinforcement learning
+relying on deep neural networks to learn a the value function.  These approaches
+rely on having a large number of datapoints to converge toward a good function
+approximator. However, in many applications and especially in HRI, these amounts
+of data are not available or obtainable due to practical constraints.
+Furthermore, human responses are often noisy and lack consistency, so methods
+are needed which can generalise from a low number of noisy data points.
 
@@
 
-In this paper we propose to use a human user to highlight the relevant features of
-the environment to reduce the state dimension of the points only to relevant
-information.
-We introduce the concept of a partial state, a sliced version of the state defined
-only on a subset of the dimensions of the state. This shifts the (state, action)
-pair paradigm to (partial state, action)  
-and in the case of RL, the tuple (state, action, reward) to (partial state,
-action, reward). This allows to compare the current state and the
-datapoints only on relevant features for action selection.
-
-\begin{comment}
-%===============================================================================
-\section{Methodology}
-
-Similarly to a SPARC setup, the supervisor can select actions, or when presented
-with an action about to be executed by the robot either cancel it or let
-it be executed.
-
-In addition to these actions, the supervisor can use the GUI to select features
-of the environment that can be sent to the algorithm to reduce the state associated
-to this action to a partial state. Similarly, the algorithm can indicate which
-parts of the states have been used for the selection to the supervisor who can
-correct them while the action is being executed.
-
-%Example?
-\end{comment}
+In this paper we propose to use a human user to highlight the relevant features
+of the environment to reduce the state dimension of the points only to relevant
+information.  We introduce the concept of a partial state, a sliced version of
+the state defined only on a subset of the dimensions of the state. This shifts
+the (state, action) pair paradigm to (partial state, action)  and in the case of
+RL, the tuple (state, action, reward) to (partial state, action, reward). This
+allows to compare the current state and the datapoints only on relevant features
+for action selection.
 
@@
 to a set of actions $\mathcal{A}$ and a state $\mathcal{S} \in [0,1]^{n}$. We
-also define the partial states $\mathcal{S'} \in [0,1]^{n'}$ with $n' \leq n$ as a
-slice of $\mathcal{S}$, a subset of $\mathcal{S}$ where some dimensions have
+also define the partial states $\mathcal{S'} \in [0,1]^{n'}$ with $n' \leq n$ as
+a slice of $\mathcal{S}$, a subset of $\mathcal{S}$ where some dimensions have
 been removed. 
@@
 associated with the partial state $s'$. For example, a state $s$ could be
-defined in 4 dimensions such as ${s=[1,0.2,0,0.5]}$, and $s'$ in two dimensions with
-${s'=[-,0.2,0,-]}$ with symbol '$-$' reprensenting the dimensions removed. For
-the learning algorithm, this means that the action $a$ has been evaluated $r$ in
-the partial state $s'$.
+defined in 4 dimensions such as ${s=[1,0.2,0,0.5]}$, and $s'$ in two dimensions
+with ${s'=[-,0.2,0,-]}$ with symbol '$-$' reprensenting the dimensions removed.
+For the learning algorithm, this means that the action $a$ has been evaluated
+$r$ in the partial state $s'$.
 
-To each action
-$a \in \mathcal{A}$ we can associate a set $\mathcal{C}_{a}$ of pairs $(s',r)$
-representing the rating done by the supervisor to action $a$ with features
-highlighted for the multiple $s'$. When adding a new pairt $(s',r)$, we can discard potential
-previous pairs with an identical $s'$ to represent the evolution of the policy
-evaluation by the supervisor.
+To each action $a \in \mathcal{A}$ we can associate a set $\mathcal{C}_{a}$ of
+pairs $(s',r)$ representing the rating done by the supervisor to action $a$ with
+features highlighted for the multiple $s'$. When adding a new pair $(s',r)$, we
+can discard potential previous pairs with an identical $s'$ to represent the
+evolution of the policy evaluation by the supervisor.
 
@@
 
-When facing a new state $s$ where an action has to be
-selected, the agent can select an action following Algorithm~\ref{algo}. For
-each action $a \in \mathcal{A}$, we take the pair $(s',r)$ with the closest $s'$
-to the current state (as defined by normalised distance over the dimensions
-where $s'$ is defined). That way, each action $a$ can be associated to an
-expected reward defined by the product between the similarity of the closest
-partial state known for $a$ and the reward obtained for executing $a$ in that partial state.
+When facing a new state $s$ where an action has to be selected, the agent can
+select an action following Algorithm~\ref{algo}. For each action $a \in
+\mathcal{A}$, we take the pair $(s',r)$ with the closest $s'$ to the current
+state (as defined by normalised distance over the dimensions where $s'$ is
+defined). That way, each action $a$ can be associated to an expected reward
+defined by the product between the similarity of the closest partial state known
+for $a$ and the reward obtained for executing $a$ in that partial state.
 Finally, the action with the highest expected reward can be selected.
@@
 
-SPARC has been shown to be compatible with RL in \cite{senft2017supervised},
-and can also be easily combined with the approach presented in this paper using
+SPARC has been shown to be compatible with RL in \cite{senft2017supervised}, and
+can also be easily combined with the approach presented in this paper using
 partial states. For example, when selecting an action for the robot to be
 executed, the supervisor can also select which features in the environment
-should be selected as the partial state, and this associates the reward 
-to this action in this partial state. Similarly, when an action is
-proposed to the supervisor the features represented by the dimensions of the
-closest partial state for this action can be exposed to the supervisor as a way to explain why
+should be selected as the partial state, and this associates the reward to this
+action in this partial state. Similarly, when an action is proposed to the
+supervisor the features represented by the dimensions of the closest partial
+state for this action can be exposed to the supervisor as a way to explain why
 this action has been selected. Facing this, the supervisor can: (1) not react,
 allowing the action to be executed and associating a reward of +1 to the partial
-state and the action proposed, (2) change the partial state to correct the features
-related to this action or (3) cancel it, preventing the execution and associating a
-reward of -1 to the partial state identified by the robot or the supervisor.
+state and the action proposed, (2) change the partial state to correct the
+features related to this action or (3) cancel it, preventing the execution and
+associating a reward of -1 to the partial state identified by the robot or the
+supervisor.
 
@@
 
-An example of an application is a social robot which interacts with children in an educational scenario.
-The robot plays an educational game with children to teach them notions about
-diverse topics according to the needs of the teacher. For this example, a child
-and a robot are playing a game about the food web, teaching wich animals eat which
-ones on a Sandtray~\cite{baxter2012touchscreen}. In addition to the child and
-the robot, an adult supervises the robot using a tablet with a Graphical User
-Interface (GUI) to teach the robot how to interact with the child as shown in
-Figure~\ref{fig:setup}.
+An example of an application is a social robot which interacts with children in
+an educational scenario.  The robot plays an educational game with children to
+teach them notions about diverse topics according to the needs of the teacher.
+For this example, a child and a robot are playing a game about the food web,
+teaching which animals eat which ones on a Sandtray~\cite{baxter2012touchscreen}.
+In addition to the child and the robot, an adult supervises the robot using a
+tablet with a Graphical User Interface (GUI) to teach the robot how to interact
+with the child as shown in Figure~\ref{fig:setup}.
 
@@
 %===============================================================================
-\begin{comment}
-\section{Challenges}
-
-A large body of the
-Interactive Machine Learning research is focused on simple inputs from the
-humans, such as providing labels \cite{cakmak2012designing}, rewards
-\cite{knox2009interactively} or kinesthetic demonstrations
-\cite{billard2008robot}. However, as stated in \cite{amershi2014power}: "people
-want to demonstrate how learners should behave" and "users may desire richer
-control over machine-learning systems than simply labeling data". Human teachers
-want to be more active and involved in the teaching process, to make their
-student learning faster. 
-And, as shown in \cite{senft2017supervised}, providing teacher with this control
-can keep the agent in relevant states of the environment, speeding the learning
-and reducing the risk to have the robot execute undesired actions.
-
-In human social learning, both interactants have access to a similar set of
-inputs: the senses available to a human body, and the teacher has additional
-knowledge about the environment that can be communicated in an open ended way to
-the learner. On the other in human-robot teaching, the way to sense the world
-can be highly different between the two partners, and as of today, there is no
-open ended way of communicating new concepts or explication as natural langage
-processing is not yet solve. This creates two main challenges to make robot
-learning for human use complex inputs: 
-\begin{itemize}
-    \item Having a mapping between the action state space of the human and the
-            robot ensuring that feature used for action selection for one
-            interactant are available to the other.
-    \item Communicating these features from one participant to the other: allow
-        the robot to make sense of the human's instructions and the human to
-        understand the robot's intentions.
-\end{itemize}
-\end{comment}
 \section{Future work}
@@
 
-The current work could also be extended to allow the agent to continue to improve its
-behaviour even in the absence of a supervisor, progressively exploring around the
-learnt policy improving its behaviour beyond the demonstrations. This
-could be done by allowing the supervisor to provide rewards during the learning
-phase and combine these rewards with the demonstrations to learn a reward
-function in a fashion similar to Inverse Reinforcement Learning
-\cite{abbeel2004apprenticeship} or TAMER \cite{knox2009interactively}. This
-could also use partial states associated to these rewards to ease the
-generalisation of the reward function with only a low number of datapoints.
-But without the supervisor, the assumption that only a
-myopic action selection is sufficient would not hold anymore and the problem of
-delayed rewards would have to be tackled.
+The current work could also be extended to allow the agent to continue to
+    improve its behaviour even in the absence of a supervisor, progressively
+    exploring around the learnt policy improving its behaviour beyond the
+    demonstrations. This could be done by allowing the supervisor to provide
+    rewards during the learning phase and combine these rewards with the
+    demonstrations to learn a reward function in a fashion similar to Inverse
+    Reinforcement Learning \cite{abbeel2004apprenticeship} or TAMER
+    \cite{knox2009interactively}. This could also use partial states associated
+    to these rewards to ease the generalisation of the reward function with only
+    a low number of datapoints.  But without the supervisor, the assumption that
+    only a myopic action selection is sufficient would not hold anymore and the
+    problem of delayed rewards would have to be tackled.
 %===============================================================================
-%\section{Conclusion}
-%\label{sec:conclusion}
+    %\section{Conclusion} \label{sec:conclusion}
     %==============================================================================
-\section{Acknowledgments}
-This work was supported by the EU FP7 DREAM project (grant no.  611391) and EU
-H2020 Marie Sklodowska-Curie Actions project DoRoThy (grant 657227).
+\section{Acknowledgments} This work was supported by the EU FP7 DREAM project
+    (grant no.  611391) and EU H2020 Marie Sklodowska-Curie Actions project
+    DoRoThy (grant 657227).
 

### 2017-08-22 paper.tex
to fu

@@
 
-\maketitle \begin{abstract}
-%As robots will integrate human society, they will have to satify humans'
-    %expectations. However at the design time, it seems hardly possible to know
-    %in advance exactly all the behaviours expected from the robot. As such to
-    %be accepted in human society robots have to learn how to interact with
-    %humans.
+\maketitle
+
+\begin{abstract}
+
     Social interacting is a complex task for which machine learning holds
@@
     policy.
+
 \end{abstract}
@@
  Similarly to  people, robots need to be able to learn how to complete tasks
- throug creating and optimising action policies. This includes learning social
+ through creating and optimising action policies. This includes learning social
  norms and how to make sense of the social world.
@@
 
-%These relevant features in the state space can be encoded in the representation of
-%the space the robot uses for action selection or be learnt. Recent successes in Deep
-%Learning~\cite{lecun2015deep} have shown that complex features can be extracted
-%by neural networks assuming that enough datapoints are available.
-
 In previous work~\cite{senft2015sparc,senft2017supervised}, we introduced the
@@
 
-===============================================================================
+%===============================================================================
 
@@
 
-%Classic approaches in RL generally rely on exploring virtual environments where
-%the agent tries to maximise the reward.
 In many cases where RL achieves success, the agent has access to a virtual
@@
 \subsubsection{Design decisions:}
+
 Initial knowledge has to be used in the design of the algorithm, the
 representation of the state and actions spaces and the reward funtion. For
-example, only carefully crafted features allowed
-Tesauro to improve its algorithm for Backgammon from a intermediate-level player
-to super-human level~\cite{tesauro1995temporal}. Similarly, the design of
-complex neural networks for state generalisation, the representation of actions
-as motor primitives rather than raw motor angles or adding additional
-information in the reward function have important impacts on the ability of
-the robot to reach a successful policy~\cite{kober2013reinforcement}.
+example, only carefully crafted features allowed Tesauro to improve its
+algorithm for Backgammon from a intermediate-level player to super-human
+level~\cite{tesauro1995temporal}. Similarly, the design of complex neural
+networks for state generalisation, the representation of actions as motor
+primitives rather than raw motor angles or adding additional information in the
+reward function have important impacts on the ability of the robot to reach a
+successful policy~\cite{kober2013reinforcement}.
 
 \subsubsection{Demonstrations:}
-Initial knowledge can be provided to the agent
-through demonstrations. These demonstrations can be used to create an initial
-policy which is sufficiently efficient to start interacting in the environment
-and gather information to improve over time. This initial policy, required to
-receive meaningful feedback from the environment can be impossible to reach by
-relying only on random exploration and feedback from the environment. For
-example the game of Go in its larger board size contains more than $10^{210}$
-states, so exhaustive search is not possible.  Silver et al.
-\cite{silver2016mastering} started with supervised learning from Go masters'
-games to learn a decent enough policy and then proceeded using deep learning,
-self play and tree search to achieve super-human capabilities and beating the
-best human players.
+
+Initial knowledge can be provided to the agent through demonstrations. These
+demonstrations can be used to create an initial policy which is sufficiently
+efficient to start interacting in the environment and gather information to
+improve over time. This initial policy, required to receive meaningful feedback
+from the environment can be impossible to reach by relying only on random
+exploration and feedback from the environment. For example the game of Go in its
+larger board size contains more than $10^{210}$ states, so exhaustive search is
+not possible.  Silver et al.~\cite{silver2016mastering} started with supervised
+learning from Go masters' games to learn a decent enough policy and then
+proceeded using deep learning, self play and tree search to achieve super-human
+capabilities and beating the best human players.
 
@@
 \subsubsection{Guiding the learning:}
+
 Rather than solely providing initial knowledge to the agents, humans can also
@@
 A first approach consists in sequencing the tasks the robot will face.  This
-approach, known as ``scaffolding'' \cite{saunders2006teaching}, progressively
+approach, known as ``scaffolding''~\cite{saunders2006teaching}, progressively
 increases the difficulty and complexity of the task as the robot is learning to
@@
 
-In \cite{senft2015sparc}, we introduced the Supervised Progressively Autonomous
+In~\cite{senft2015sparc}, we introduced the Supervised Progressively Autonomous
 Robot Competencies (SPARC). SPARC relies on a supervisor with the ability to
@@
 
-%SPARC has been designed with the idea of teaching a robot to interact with humans,
-%it is specially usefull when the frequency of action selection is low (less than
-%1Hz) so action can be evaluated by a human before being executed, when the agent
-%has to learn with a limited number of datapoints and when
-%undesired actions executed by an agent can have a high cost and are to be
-%avoided.
-
-In \cite{senft2017supervised}, we presented a way to combine SPARC and RL, by
+In~\cite{senft2017supervised}, we presented a way to combine SPARC and RL, by
 assigning a positive reward to every action executed by the robot, making the
@@
 are needed which can generalise from a low number of noisy data points.
-
-%In \cite{sutton1996generalisation}, Sutton proposed to use sparse coarse
-%coding
-%dividing the state in slices and tiles as a way to generalise quickly for
-%continuous spaces in RL.
 
@@
 
-SPARC has been shown to be compatible with RL in \cite{senft2017supervised}, and
+SPARC has been shown to be compatible with RL in~\cite{senft2017supervised}, and
 can also be easily combined with the approach presented in this paper using
@@
 
-The GUI (Figure \ref{fig:gui}) is an augmented
-version of the game itself, which can be use to make the robot move items on the
-game by dragging them on the GUI or which can display actions proposed by the
-robot with a cancel button to refuse an action. For example in
-Figure~\ref{fig:gui} the robot proposes to move the eagle to the rat, and
-highlight (as shown by blue circles) the eagle and the rat. This indicate that
-features relevant to the eagle and the rat have been used to select this action.
+The GUI (Figure~\ref{fig:gui}) is an augmented version of the game itself, which
+can be use to make the robot move items on the game by dragging them on the GUI
+or which can display actions proposed by the robot with a cancel button to
+refuse an action. For example in Figure~\ref{fig:gui} the robot proposes to move
+the eagle to the rat, and highlight (as shown by blue circles) the eagle and the
+rat. This indicate that features relevant to the eagle and the rat have been
+used to select this action.
 
@@
 exploring around the learnt policy improving its behaviour beyond the
-    demonstrations. This could be done by allowing the supervisor to provide
-    rewards during the learning phase and combine these rewards with the
-    demonstrations to learn a reward function in a fashion similar to Inverse
-    Reinforcement Learning \cite{abbeel2004apprenticeship} or TAMER
-    \cite{knox2009interactively}. This could also use partial states associated
-    to these rewards to ease the generalisation of the reward function with only
-    a low number of datapoints.  But without the supervisor, the assumption that
-    only a myopic action selection is sufficient would not hold anymore and the
-    problem of delayed rewards would have to be tackled.
-%===============================================================================
-    %\section{Conclusion} \label{sec:conclusion}
+demonstrations. This could be done by allowing the supervisor to provide rewards
+during the learning phase and combine these rewards with the demonstrations to
+learn a reward function in a fashion similar to Inverse Reinforcement
+Learning~\cite{abbeel2004apprenticeship} or TAMER ~\cite{knox2009interactively}.
+This could also use partial states associated to these rewards to ease the
+generalisation of the reward function with only a low number of datapoints.  But
+without the supervisor, the assumption that only a myopic action selection is
+sufficient would not hold anymore and the problem of delayed rewards would have
+to be tackled.
+
 %==============================================================================
 \section{Acknowledgments} This work was supported by the EU FP7 DREAM project
-    (grant no.  611391) and EU H2020 Marie Sklodowska-Curie Actions project
-    DoRoThy (grant 657227).
+(grant no.  611391) and EU H2020 Marie Sklodowska-Curie Actions project DoRoThy
+(grant 657227).
 

### 2017-08-22 paper.tex
Early updates based on reviews

@@
 guide it to the desired behaviour. Unlike other RL setups, with TAMER, the
-reward is not provided by the environment but by a human observer. With this
-approach the teacher can adapt the rewards to the current policy and performance
-of the agent, for example starting to positively reward suboptimal behaviours
-that are better than the current policy and later, as the agent improves its
-behaviour, reward these same suboptimal behaviours negatively and only the
-optimal ones positively.
+reward is not provided by the environment but by a human observer. TAMER derives
+a reward function from the human feedbacks and uses this function to evaluate
+the current behaviour. In a similar approach, MacGlashan et al. proposed COACH
+in~\cite{macglashan2017interactive}. COACH assumes that human rewards represent
+the advantage function, i.e. how much the current action is better than the
+current policy. With COACH, the teacher can adapt the rewards to the current
+policy and performance of the agent, for example starting to positively reward
+suboptimal behaviours that are better than the current policy and later, as the
+agent improves its behaviour, reward these same suboptimal behaviours negatively
+and only the optimal ones positively.
 
@@
 actions are useful, the learning can be faster than autonomous learning or
-feedback based learning as illustrated in Figure~\ref{fig:comparison}.
+learning based on human feedback as illustrated in Figure~\ref{fig:comparison}.
+In Autonomous Learning, the agent has first to discover its environment to start
+gathering relevant feedbacks, leading to a low initial performance and a slow
+improvement in early stage of learning. With a teaching based on human
+feedbacks, the teacher can quickly provide feedbacks on actions to reach more
+quickly an efficient policy. However, as the teacher only provide feedbacks and
+cannot prevent the agent to make mistakes, the initial performance can be poor.
+On the other hand, SPARC, with the control of the teacher over the executed
+actions can prevent the agent to make mistakes in early stages, achieving a high
+performance even at the start of the learning. The total blending between
+autonomous execution of actions and demonstrations and the control over
+\emph{every} actions executed by the agent are the specificities of SPARC
+compared to other approaches using humans to guide the learning of an agent.
 
@@
     autonomy and human workload for an autonomous learner, an approach using
-    human rewards, and SPARC.}
+    human feedbacks, and SPARC.}
     \label{fig:comparison}
@@
 or non-deterministic transitions from one state to another, elements which are
-typically present in social interactions.
+typically present in social interactions. Similarly to TAMER or COACH, this
+approach allows to reproduce an action policy from a teacher even in the absence
+of a reward function, but as the teacher has control over the robot actions, the
+learning can be faster and safer.
 
@@
 requires a way to generalise knowledge to unseen states. A classic approach is
-to use a feed-forward neural network or to use deep reinforcement learning
-relying on deep neural networks to learn a the value function. These approaches
-rely on having a large number of datapoints to converge toward a good function
-approximator. However, in many applications and especially in HRI, these amounts
-of data are not available or obtainable due to practical constraints.
+to use a feed-forward neural network or deep learning to learn a the value
+function generalising to unseen states. Neural network rely on having a large
+number of datapoints to converge toward a good function approximator.
+Alternatively, Cobo et al. proposed in~\cite{cobo2011automatic} to abstract
+features automaticly from demonstrations to learn faster. But even in this case,
+the number of datapoints required is still high (around 1000 samples per
+participants). However, in many applications and especially in HRI, these
+amounts of data are not available or obtainable due to practical constraints.
 Furthermore, human responses are often noisy and lack consistency, so methods
@@
 credit assignment for delayed rewards can be ignored which allows us to consider
-only a myopic approach.
+only a myopic approach in a fashion similar to TAMER~\cite{knox2009interactively}.
 
@@
         }
-        compute expected reward $\hat{r}(a)$ for taking $a$ in $s$:
-        $\hat{r}(a) = max(\Delta) \cdot r(arg\, max_{p} \Delta(p))$\\
-        with $r(\Delta(p))$ the reward of $p = (s',r)$ 
+        find closest pair $\hat{p}$:\\
+        $\hat{p} = arg\, max_{p} \Delta(p)$\\
+        compute expected reward $\hat{r}(a)$ for taking $a$ in $s$:\\
+        $\hat{r}(a) = \Delta (\hat{p}) \cdot r(\hat{p})$\\
+        with $r(p)$ the reward of $p = (s',r)$ 
     }
@@
 When facing a new state $s$ where an action has to be selected, the agent can
-select an action following Algorithm~\ref{algo}. For each action $a \in
-\mathcal{A}$, we take the pair $(s',r)$ with the closest $s'$ to the current
-state (as defined by normalised distance over the dimensions where $s'$ is
-defined). That way, each action $a$ can be associated to an expected reward
-defined by the product between the similarity of the closest partial state known
-for $a$ and the reward obtained for executing $a$ in that partial state.
-Finally, the action with the highest expected reward can be selected.
+select an action following Algorithm~\ref{algo} in a instance-based learning
+fashion. For each action $a \in \mathcal{A}$, we take the pair $(s',r)$ with the
+closest $s'$ to the current state (as defined by the average quadratic distance
+over the normalised dimensions where $s'$ is defined). That way, each action $a$
+can be associated to an expected reward defined by the product between the
+similarity of the closest partial state known for $a$ and the reward obtained
+for executing $a$ in that partial state.  Finally, the action with the highest
+expected reward can be selected.
+
+The normalisation of each dimension of the state allows distances to be
+comparable as values on all dimensions have the same range. Additionally taking
+the average quadratic distance over each defined dimension allows to compare
+distances even when states are defined on a different number of dimensions.
 

### 2017-08-23 paper.tex
Further updates

@@
 
-Initial knowledge is often a crucial step to allow an algorithm to learn an
+Initial knowledge is often crucial to allow an algorithm to learn an
 efficient action policy. This knowledge, originating from human expertise, can
@@
 
-Approaches from animal conditioning have also been transfered to Machine
-Learning. For example, the TAMER framework~\cite{knox2009interactively} is an
-adaptation of ``shaping'', tuning an animal's behaviour by providing rewards to
-guide it to the desired behaviour. Unlike other RL setups, with TAMER, the
-reward is not provided by the environment but by a human observer. TAMER derives
-a reward function from the human feedbacks and uses this function to evaluate
-the current behaviour. In a similar approach, MacGlashan et al. proposed COACH
+Agents learning in environments providing rewards can also benefit from
+additional rewards from human teachers. Depending on the task and the
+environment, different ways exist to combine rewards from multiple sources, and
+studies show that augmenting rewards from the environment by human ones can
+speed up the learning and reduce the number of undesired behaviours~
+\cite{griffith2013policy,knox2010combining,judah2010reinforcement}.
+
+When environments do not supply rewards, they can be replaced by human ones. For
+example, the TAMER framework~\cite{knox2009interactively} derives a reward
+function from the human feedbacks and uses this function to evaluate the current
+behaviour. In a similar approach, MacGlashan et al. proposed COACH
 in~\cite{macglashan2017interactive}. COACH assumes that human rewards represent
 the advantage function, i.e. how much the current action is better than the
-current policy. With COACH, the teacher can adapt the rewards to the current
-policy and performance of the agent, for example starting to positively reward
-suboptimal behaviours that are better than the current policy and later, as the
-agent improves its behaviour, reward these same suboptimal behaviours negatively
-and only the optimal ones positively.
+current policy, allowing to adapt the reward function to the strategies used and
+the current state of the learner.
 
@@
 actions can prevent the agent to make mistakes in early stages, achieving a high
-performance even at the start of the learning. The total blending between
-autonomous execution of actions and demonstrations and the control over
-\emph{every} actions executed by the agent are the specificities of SPARC
-compared to other approaches using humans to guide the learning of an agent.
+performance even at the start of the learning.
+
+Compared to similar algorithms
+\cite{chernova2009interactive,walsh2010generalizing}, which allows the agent to
+request demonstrations and/or the teacher to provide demonstrations to correct
+mistakes made by the robot, SPARC allows the teacher to correct any  action
+before its execution, thus reducing importantly the risk of the agent making
+errors. The total blending between autonomous execution of actions and
+demonstrations and the control over \emph{every} actions executed by the agent
+are the specificities of SPARC.
 
@@
 allows to compare the current state and the datapoints only on relevant features
-for action selection.
+for action selection. With this instance-based method~\cite{aha1991instance},
+the algorithm can have a state abstraction allowing it to generalise even with a
+few datapoints instead of the large numbers normally required to abstract
+features from examples.
 
@@
 the average quadratic distance over each defined dimension allows to compare
-distances even when states are defined on a different number of dimensions.
-
-%When selecting an action, the agent can also use
-%the dimensions of the close state $s'$ used for the selection to indicate the
-%supervisor which parts of the state have been used for the action selection.
+similarities even when states are defined on a different number of dimensions.
 

### 2017-08-28 paper.tex
Update on Overleaf.

@@
     interact with the social world. As such we argue that robots will profit
-    from human expertise and guidance to learn social interactions. And as the
+    from human expertise and guidance to learn social interactions. However, as the
     quantity of input a human can provide is limited, new methods have to be
@@
     Autonomous Robot Competencies (SPARC), which allows safer online learning
-    with Reinforcement Learning, with the use partial states rather than full
-    states to accelerate generalisation and obtain more quickly a usable action
-    policy.
+    with Reinforcement Learning, with the use of partial states rather than full
+    states to accelerate generalisation and obtain a usable action
+    policy more quickly.
 
@@
 In previous work~\cite{senft2015sparc,senft2017supervised}, we introduced the
-Supervised Progressively Autonomous Robot Competencies (SPARC), a way to teach a
+Supervised Progressively Autonomous Robot Competencies (SPARC) as a way to teach a
 robot an action policy while interacting based on a human supervisor intervening
@@
 the environment relevant for the selected action. During the action selection
-phase, the robot can compare these features, defined as partial states, with the
+phase, the robot can compare these features, defined as \textit{partial states}, with the
 current state to select an action. The selected action is presented to the human
-supervisor, who can either correct the action or approve it for execution.
+supervisor, who can either correct the proposed action or approve it for execution.
 
@@
 proceeded using deep learning, self play and tree search to achieve super-human
-capabilities and beating the best human players.
+capabilities and the capacity to beat the best human players.
 
@@
 Another approach to guide the learning is to bias the action selection.
-In~\cite{thomaz2008teachable}, the authors propose to use a human supervisor to
+In~\cite{thomaz2008teachable}, the authors propose using a human supervisor to
 supply an agent with both rewards and potential guidance indicating what the
@@
 decisions, the robot learns which actions are desired and can as such refine its
-policy over time reducing the need for the supervisor to correct or select an
+policy over time, thus progressively reducing the need for the supervisor to correct or select an
 action.
@@
 In Autonomous Learning, the agent has first to discover its environment to start
-gathering relevant feedbacks, leading to a low initial performance and a slow
-improvement in early stage of learning. With a teaching based on human
-feedbacks, the teacher can quickly provide feedbacks on actions to reach more
-quickly an efficient policy. However, as the teacher only provide feedbacks and
-cannot prevent the agent to make mistakes, the initial performance can be poor.
+gathering relevant feedback, leading to a low initial performance and a slow
+improvement in early stage of learning. With teaching based on human
+feedback, the teacher can quickly provide information on actions to reach an efficient policy more
+quickly. However, as the teacher only provides feedback and
+cannot prevent the agent making mistakes, the initial performance can be poor.
 On the other hand, SPARC, with the control of the teacher over the executed
-actions can prevent the agent to make mistakes in early stages, achieving a high
+actions, can prevent the agent from making mistakes in early stages, achieving a high
 performance even at the start of the learning.
@@
     autonomy and human workload for an autonomous learner, an approach using
-    human feedbacks, and SPARC.}
+    human feedback, and SPARC.}
     \label{fig:comparison}
 \end{figure}
+%PEB: in the figure "feedbacks" should be "feedback"
 
@@
 assumption that every action has been explicitly or implicitely approved by the
-supervisor. However this method was directly mapping a single (state, action)
+supervisor. However this method directly mapped a single (state, action)
 pair to a reward without making use of any kind of generalisation. As such it
@@
 to use a feed-forward neural network or deep learning to learn a the value
-function generalising to unseen states. Neural network rely on having a large
+function generalising to unseen states. Neural networks rely on having a large
 number of datapoints to converge toward a good function approximator.
 Alternatively, Cobo et al. proposed in~\cite{cobo2011automatic} to abstract
-features automaticly from demonstrations to learn faster. But even in this case,
+features automatically from demonstrations to learn faster. But even in this case,
 the number of datapoints required is still high (around 1000 samples per
-participants). However, in many applications and especially in HRI, these
+participant). However, in many applications and especially in HRI, these
 amounts of data are not available or obtainable due to practical constraints.
@@
 of the environment to reduce the state dimension of the points only to relevant
-information. We introduce the concept of a partial state, a sliced version of
+information. We introduce the concept of a \textit{partial state}, a sliced version of
 the state defined only on a subset of the dimensions of the state. This shifts
@@
 RL, the tuple (state, action, reward) to (partial state, action, reward). This
-allows to compare the current state and the datapoints only on relevant features
+allows a comparison of the current state and the datapoints only on relevant features
 for action selection. With this instance-based method~\cite{aha1991instance},
@@
 features from examples.
+%PEB: sounds very much like the "don't care" token in learning classifier systems...
 
@@
 refuse an action. For example in Figure~\ref{fig:gui} the robot proposes to move
-the eagle to the rat, and highlight (as shown by blue circles) the eagle and the
+the eagle to the rat, and highlights (as shown by blue circles) the eagle and the
 rat. This indicate that features relevant to the eagle and the rat have been
@@
     \caption{Interface for the supervisor with an action being proposed, moving
-        the eagle to the rat with highlight of the eagle and the rat.}
+        the eagle to the rat highlighting both the eagle and the rat.}
         \label{fig:gui}
@@
 This could also use partial states associated to these rewards to ease the
-generalisation of the reward function with only a low number of datapoints.  But
+generalisation of the reward function with only a low number of datapoints. However,
 without the supervisor, the assumption that only a myopic action selection is

### 2017-08-29 paper.tex
Typos

@@
 example, the TAMER framework~\cite{knox2009interactively} derives a reward
-function from the human feedbacks and uses this function to evaluate the current
+function from the human feedback and uses this function to evaluate the current
 behaviour. In a similar approach, MacGlashan et al. proposed COACH
@@
 Compared to similar algorithms
-\cite{chernova2009interactive,walsh2010generalizing}, which allows the agent to
+\cite{chernova2009interactive,walsh2010generalizing}, which allow the agent to
 request demonstrations and/or the teacher to provide demonstrations to correct
@@
         $\hat{r}(a) = \Delta (\hat{p}) \cdot r(\hat{p})$\\
-        with $r(p)$ the reward of $p = (s',r)$ 
+        with $r(p)$ the reward $r$ of the pair $p = (s',r)$ 
     }
